---
title: "BIHS_explore"
author: "Lila Cardell"
date: "October 24, 2019"
output: pdf_document
#fontsize: 11pt

#bibliography: nutrition.bibtex
---

Set working directory and install packages
```{r setup, include=FALSE}


knitr::opts_chunk$set(echo = FALSE,root.dir='C:/Users/lilac2/Box/BIHS Project',warning = FALSE, message=FALSE)
options(scipen=999)
set.seed(12345)
###  Check for and load Packages   ###

## Clear worksace
rm(list = ls())
gc()

## This function will check if a package is installed, and if not, install it
pkgTest  =  function(x) {
  if (!require(x, character.only = TRUE))
  {
    install.packages(x, dep = TRUE)
    if(!require(x, character.only = TRUE)) stop("Package not found")
  }
}

## These lines load the required packages
packages  =  c('data.table','tidyverse','haven','stargazer','plm','lubridate','survey','psych','knitr','xtable','tables','kableExtra','fuzzyjoin','MASS','matrixcalc','car','stringr','styler','readxl','magrittr','sjmisc','readxl','xlsx') ## you can add more packages here
lapply(packages, pkgTest)



```



1. Import BIHS data
```{r import BIHS data,results='hide'}
# Read in data for project

setwd("C:/Users/lilac2/Box/BIHS Project/Data")

#this pulls in all 2011 household level files except the WEAI
filenames<-grep(list.files(path="./Raw Data/bihs_2011_2012/household/data"),pattern=c("weai","h"),inv=TRUE,value=TRUE)
names<-gsub(".dta","",filenames)

 for(i in names){
   filepath <- file.path(paste("./Raw Data/bihs_2011_2012/household/data/",i,".dta",sep=""))
   assign(paste(substring(i,9),"_2011",sep=""),haven::read_dta(filepath))
 }


#read in the 2011 census and 2015 consumption file for now
#census_2011 = read_dta("./Raw Data/bihs_2011_2012/census/data/001_census_ftf.dta")

x1_1_f_2015 = read_dta("./Raw Data/bihs_2015/household/data/064_r2_mod_x1_1_female.dta")




#import names of menu items from the 2015 codebook
#this is assumed to be more comprehensize than 2011 and also available in excel
menucodes = read_excel("./Raw Data/bihs_2015/household/documents/000_codebook.xls", 
                       sheet = "064_r2_mod_x1_1_female", range = "C31:D415",col_names = c("menuname","menu"))


#count menu items
menu_items = aggregate(a01~menu, data=x1_female_2011, FUN = length)%>%
  left_join(menucodes,by=c("menu"))%>%
dplyr::rename("menucode"="menu","hh_num" = "a01")%>%
  arrange(desc(hh_num))
#206 items consumed in 2011
#issue with salt not being separated into iodine/non-iodine in 2011
#menu_items = aggregate(a01~x1_05, data=x1_1_f_2015, FUN = length) #180 items consumed in 2015
#1/3 salt is regular, 2/3 iodine (return to this later)


###import names of ingredient items from 2015 (assumed to be more comprehensize than 2011)
ingredientcodes = read_excel("./Raw Data/bihs_2015/household/documents/000_codebook.xls", 
                             sheet = "064_r2_mod_x1_1_female", range = "C417:D717", col_names =c("ingredientname","ingredient"))%>%
 add_row(ingredientname="Salt",ingredient=252)

occupationcodes=read_excel("./Raw Data/bihs_2015/household/documents/000_codebook.xls", 
                             sheet ="003_r2_male_mod_b1", range = "C106:D182", col_names = c("occupation_name","occupation_code"))




rm(filenames,filepath,i,names,x1_1_f_2015)

```

2. Import FCT Data
```{r import FCT Data,results='hide'}

setwd("C:/Users/lilac2/Box/BIHS Project/Data")
###Import nutrition data
FCT_bangladesh =read_excel("./Clean Data/Nutrient Table/FCDB_7_4_14_LC.xlsx",sheet = "UserDB_Main_table")

#drop extra rows of nutrient data and select/rename/convert variables
nutrients = left_join(ingredientcodes,FCT_bangladesh,by=c("ingredient"="BIHS_code")) %>%
  dplyr::rename(foodname_english=4,foodname_bengali=5,edible=8,kcal=9,water=11,protein=12,fat=13,carb=14,calcium=17,iron=18)%>% 
  dplyr::select(2,1,4,8:9,11:14,17,18)%>% 
 mutate_at(vars(4:11),as.numeric,na.omit=TRUE)
 
rm(FCT_bangladesh)
```


3. Calculate calories for each recipe
```{r calculate recipe calories}
 
#join recipe dataset with menucodes to include menu names
x1_f_2011_m = left_join(x1_female_2011,menucodes,by=c("menu"))%>%
  mutate(date=as_date(paste(x1_yy, x1_mm, x1_dd,sep="-")))%>%
  dplyr::rename(rid=x1_rid,time=x1_03,menucode=menu,foodsource=x1_02,menucookwt=cwgt)%>%
  dplyr::select(1,41,6,43,8,7,9,42,12,contains("x1_07"),contains("x1_08"))%>%
  filter(!menucode %in% c(252,2521,2522))

#rename variables with ingredient codes and weights to help with reshaping dataset 
names(x1_f_2011_m)<-gsub("x1_07","icode",names(x1_f_2011_m))
names(x1_f_2011_m)<-gsub("x1_08","iweight",names(x1_f_2011_m))
names(x1_f_2011_m)<-gsub("_0","_",names(x1_f_2011_m))


#reshape the recipe dataset to join it with the nutrient dataset
#edit codes ingredients which have two BIHS codes, but are the same thing

nutnames=names(dplyr::select(nutrients,5,7:11))

recipes=melt(setDT(x1_f_2011_m),measure.vars=patterns("icode","iweight"),variable.name="inumber",value.name=c("icode","iweight"))%>%
  arrange(a01,date,time,menucode)%>%
  filter(is.finite(icode))%>%
  mutate(icode=recode(icode,"233=232;90=80;193=181;187=186;32=258;47=46;267=162;188=189;211=179;25=157;204=179;238=189;229=228;126=123;111=88;2521=252;2522=252;41=249"))%>%
  mutate(icode=as.numeric(icode))%>%
  left_join(nutrients,by=c("icode"="ingredient"))

#calculate the specific per gram nutrient input of each ingredient: nutrient_c = (ingredient weight in grams x nutrientval per 100g)/100
for (x in nutnames){
 recipes[[paste(x,"c",sep="_")]]<-recipes[[x]]*recipes$iweight/100
}

# #the below code worked for recoding over strings/variables, but I no longer needed it after I melted wide into long but wanted to save it for future
# namesx = names(dplyr::select(x1_f_2011_m,starts_with("x1_07_")))
# 
# for(i in namesx){
# x1_f_2011_m[[i]] = recode(x1_f_2011_m[[i]],"233=232;90=80;193=181;187=186;32=258;47=46;267=162;188=189;211=179;25=157;204=179;238=189;229=228;126=123;111=88;2521=252;2522=252")
# }


#investigate ingredients that are missing nutrient info
missing = recipes[is.na(recipes$kcal),]
missing_ingredients = aggregate(a01~icode+ingredientname, data=missing, FUN = length) %>%
  arrange(desc(a01))

#sum nutrients over meal
recipe_sum=recipes%>%
  group_by(a01,sample_type,rid,date,time,foodsource,menucode,menuname,menucookwt)%>%
  #filter(!is.na(kcal))%>%    #need to find these ingredients eventually
 dplyr::summarise(sum_iweight=sum(iweight),sum_water=sum(water),sum_kcal=sum(kcal_c),sum_protein=sum(protein_c),sum_fat=sum(fat_c),sum_carb=sum(carb_c),sum_calcium=sum(calcium_c),sum_iron=sum(iron_c))


#find the median per gram nutrient info for each meal and the IQR
recipe_med=recipe_sum%>%
  group_by(menucode,menuname)%>%
  dplyr::summarise(med_kcal=median(sum_kcal/menucookwt,na.rm=TRUE),sd_kcal=sd(sum_kcal/menucookwt,na.rm=TRUE),
                   med_protein=median(sum_protein/menucookwt,na.rm=TRUE),sd_protein=sd(sum_protein/menucookwt,na.rm=TRUE),
                   med_fat=median(sum_fat/menucookwt,na.rm=TRUE),sd_fat=sd(sum_fat/menucookwt,na.rm=TRUE),
                   med_carb=median(sum_carb/menucookwt,na.rm=TRUE),sd_carb=sd(sum_carb/menucookwt,na.rm=TRUE),
                   med_calcium=median(sum_calcium/menucookwt,na.rm=TRUE),sd_calcium=sd(sum_calcium/menucookwt,na.rm=TRUE),
                   med_iron=median(sum_iron/menucookwt,na.rm=TRUE),sd_iron=sd(sum_iron/menucookwt,na.rm=TRUE))%>%
  filter_all(all_vars(!is.na(.)))

for (x in nutnames){
 recipe_med[[paste("min",x,sep="_")]]<-recipe_med[[paste("med",x,sep="_")]]-2*recipe_med[[paste("sd",x,sep="_")]]
 recipe_med[[paste("max",x,sep="_")]]<-recipe_med[[paste("med",x,sep="_")]]+2*recipe_med[[paste("sd",x,sep="_")]]
}



#add the median per gram nutrient info back into the recipe set and replace missing items and items more/less than two sd from the mean
recipe_hh=left_join(recipe_sum,recipe_med,by=c("menucode","menuname"))


for (x in nutnames){
recipe_hh[[paste("sum",x,sep="_")]]=if_else(recipe_hh[[paste("sum",x,sep="_")]]==0|
                                    is.na(recipe_hh[[paste("sum",x,sep="_")]])| 
                                    recipe_hh[[paste("sum",x,sep="_")]]>recipe_hh[[paste("max",x,sep="_")]]|
                                    recipe_hh[[paste("sum",x,sep="_")]]<recipe_hh[[paste("min",x,sep="_")]],
                                    recipe_hh[[paste("med",x,sep="_")]]*recipe_hh$menucookwt,
                                    recipe_hh[[paste("sum",x,sep="_")]])
}

recipe_hh=recipe_hh%>%
dplyr::select(1:17)


rm(recipe_med,recipe_sum,recipes,menucodes,nutrients,missing,x1_female_2011,x1_f_2011_m,x,menu_items,ingredientcodes)
```

4. Calculate calories consumed by each individual
```{r calculate individual calories,results='hide'}
#integrate with individual consumption data set and create individual calorie consumption

# #flag for individuals without consumption data
# datacheck = x2_f_2011  %>%
#   group_by(a01,x2_01) %>%
#   summarise(mealdata = n())%>%
#   filter(x2_01<100)%>%
#   dplyr::rename(mid=x2_01)

#join individual reported consumption with recipe nutrition information, and calculate individual nutrient consumption per meal item
recipe_I = left_join(x2_female_2011,recipe_hh,by=c("a01","x2_meal"="time","x2_08"="menucode"))%>%
  dplyr::rename(meal_time=x2_meal,mid=x2_01,mealtaken=x2_03,sex_guest=x2_04,age_guest=x2_05,type_guest=x2_06,menucode=x2_08,icookwt=x2_09,ilocale=x2_11,iorder=x2_12,
                sample=sample_type.x)%>%
   mutate(i_mealkcal=(icookwt/menucookwt)*sum_kcal,i_mealprotein=(icookwt/menucookwt)*sum_protein,i_mealfat=(icookwt/menucookwt)*sum_fat,
          i_mealcarb=(icookwt/menucookwt)*sum_carb,i_mealcalcium=(icookwt/menucookwt)*sum_calcium,i_mealiron=(icookwt/menucookwt)*sum_iron)%>%
  dplyr::select(-sample_type.y,-contains("sum_"))



nutrition_2011_I = recipe_I %>%
  group_by(a01, mid) %>%
  filter(mealtaken==1)%>% #filter out if meal not taken
  dplyr::summarise(mealdata=n(),I_kcal=sum(i_mealkcal,na.rm=TRUE),I_protein=sum(i_mealprotein,na.rm=TRUE),I_fat=sum(i_mealfat,na.rm=TRUE),
                   I_carb=sum(i_mealcarb,na.rm=TRUE),I_calcium=sum(i_mealcalcium,na.rm=TRUE),I_iron=sum(i_mealiron,na.rm=TRUE))%>%
  filter(mid<100) #filter out guests

nrow(filter(nutrition_2011_I,I_kcal==0|is.na(I_kcal))) #94 without calorie info

rm(recipe_I,recipe_hh)
```


****** Nutrition data comparison (TBD)
```{r food data check}
#There are multiple data sets to corroborate:
# HH reports food purchase/produced/gifted within the last 7 days on o1_female
# HH reports food group consumption over last 7 days on x3_female
# HH reports consumption over prior 24 hours on x1_female


#sevenday_items_o1 = aggregate(a01~o1_01, data=o1_female_2011, FUN = length) #295 items

#sevenday_groups_x3 = 

#oneday_items_x1 = 
  


```


5. Calculate BMI
```{r BMI calculation, include=FALSE,results='hide'}
anthro_2011_I=w1_female_2011%>%
mutate(BMI=w1_03/((w1_04/100)^2))%>%
  mutate(BMI=na_if(BMI,0),pregnant=if_else(is.na(w1_01)|w1_01==2,0,1),lactating=if_else(is.na(w1_02)|w1_02==2,0,1))%>%
 dplyr::rename(weight=w1_03,height=w1_04)%>%
  dplyr::select(-starts_with("w1_"))
  


```

6. Create Individual Roster
```{r roster_I,results='hide'}

###CREATE INDIVIDUAL ROSTER###
#add BMI and nutrition consumption to individual roster_2011         
roster_2011_I=left_join(b1_male_2011,anthro_2011_I,by=c("a01","mid","sample_type")) %>%
  dplyr::rename(hhid=a01,sex=b1_01,age=b1_02,relation=b1_03,marital=b1_04,abroad=b1_05,literacy=b1_07,
                    education=b1_08,occupation=b1_10,sampletype=sample_type) %>%
  left_join(nutrition_2011_I,by=c("hhid"="a01","mid"))
         
 
nrow(filter(roster_2011_I,is.na(mealdata))) #1158 are missing mealdata
roster_2011_I$mealdata[is.na(roster_2011_I$mealdata)] <- 0
roster_2011_I$pregnant[is.na(roster_2011_I$pregnant)] <- 0
roster_2011_I$lactating[is.na(roster_2011_I$lactating)] <- 0
nrow(filter(roster_2011_I,is.na(BMI))) #4507 are missing BMI

occupation_type = aggregate(mid~occupation, data=roster_2011_I, FUN = length) %>%
  dplyr::rename(n_I=mid)%>%
  left_join(occupationcodes,by=c("occupation"="occupation_code")) %>%
  mutate(activity=if_else(occupation %in% c(1:11,15,22,25,29:30,32:36,54,58:71),"heavy",
                          if_else(occupation %in% c(12:14,16:21,23:24,26:28,31,37:41,47,55:57,72),"moderate",
                                  "light")))%>%
  dplyr::select(1,3,2,4)

write.xlsx(occupation_type,"occupation_category.xlsx")

# add back activity level, count number of household members, and flag polygamous HH
roster_2011_I = roster_2011_I %>%
  left_join(occupation_type,by="occupation")%>%
  dplyr::select(-n_I,-occupation_name)%>%
  #filter(!relation %in% c(16)) %>%
  group_by(hhid)%>%
  mutate(hhsize=n(),
         boy=if_else(age<18 & sex==1,1,0),
         girl=if_else(age<18 & sex==2,1,0),
         man=if_else(age>=18 & sex==1,1,0),
         woman=if_else(age>=18 & sex==2,1,0),
         adult=if_else(boy==0 & girl==0,1,0),
         child=if_else(man==0 & woman==0,1,0),
         otheradult=ifelse(relation>2 & adult==1,1,0),
         porl=if_else(pregnant==1 | lactating==1,1,0),
         spouseabroad=if_else(abroad==1 & relation==2,1,0))%>%
  ungroup()%>%
  group_by(hhid,relation)%>%
  mutate(poly=if_else(n()>1 & relation==2,1,0)) %>%
  ungroup()%>%
  dplyr::select(-contains("b1"))

nrow(filter(roster_2011_I,poly==1)) #30 individuals are duplicate partners (ie: 15 hh have two spouses)
          
rm(occupation_type,occupationcodes,anthro_2011_I,nutrition_2011_I)
```

7. Create Household, Household Head, and Spouse Rosters
```{r roster_HH, echo=FALSE}

###create household level roster_2011 and add AE by OECD definition
roster_2011_hh = roster_2011_I %>%
  group_by(hhid) %>%
  dplyr::summarise(hhsize = n(), adult=sum(adult),child=sum(child), poly=max(poly),
            boy=sum(boy),girl=sum(girl),otheradult=sum(otheradult),
            porl_hh=sum(porl,na.rm=TRUE), spouseabroad_hh=sum(spouseabroad,na.rm=TRUE),
            mealdata_hhmin=min(mealdata),hh_kcal=sum(I_kcal,na.rm=TRUE),hh_protein=sum(I_protein,na.rm=TRUE),hh_fat=sum(I_fat,na.rm=TRUE),
            hh_carb=sum(I_carb,na.rm=TRUE),hh_calcium=sum(I_calcium,na.rm=TRUE),hh_iron=sum(I_iron,na.rm=TRUE),
            sampletype=first(sampletype),) %>%
  mutate(porl_hh=if_else(is.na(porl_hh),0,porl_hh),AE_OECD=1+0.7*(adult-1)+0.5*child)

#6503 households

#filter individual roster_2011 to create head and spouse roster_2011s
roster_2011_head = filter(roster_2011_I,relation==1) %>%
   mutate(agehead=age, sexhead=sex, 
          maritalhead=marital,
          abroadhead=if_else(abroad==1,1,0),
          lithead=if_else(literacy==4,1,0),
          noschoolhead=if_else(education==99,1,0),
          secondschoolhead=if_else(education %in% c(10:12,22,33),1,0),
          agworkhead=if_else(occupation %in% c(1,64:71),1,0),
          BMIhead=BMI,I_kcalhead=I_kcal) %>%
  dplyr::select(hhid,contains("head"))
#6503 heads          
          
roster_2011_spouse = filter(roster_2011_I,relation==2) %>%
            mutate(agespouse=age,sexspouse=sex,
                   abroadspouse=if_else(abroad==1,1,0),
                   litspouse=if_else(literacy==4,1,0),
                   noschoolspouse=if_else(education==99,1,0),
                   secondschoolspouse=if_else(education %in% c(10:12,22,33),1,0),
                   agworkspouse=if_else(occupation %in% c(1,64:71),1,0),
                   BMIspouse=BMI,I_kcalspouse=I_kcal)%>%
  dplyr::select(hhid,ends_with("spouse"))
#5225 spouses

#add head and spouse characteristics back to household level roster_2011                   
roster_2011_hh=full_join(roster_2011_hh,roster_2011_head,by="hhid") 
roster_2011_hh=full_join(roster_2011_hh,roster_2011_spouse,by="hhid")
#6518 households = 6503+15 additional spouses in poly hh



dupe_hh = roster_2011_hh %>%
  filter(sampletype==2 |sampletype==3)%>% 
  group_by(hhid) %>% 
  filter(n() > 1)#30 poly HH

roster_2011_hh= distinct(roster_2011_hh,hhid, .keep_all= TRUE) #keeps only one line for each poly HH because HH level var are equivalent

rm(roster_2011_head,roster_2011_spouse,dupe_hh)

```

8. Calculate village level prices and HH expenditures
```{r expenditures, echo=FALSE,include=FALSE,results='hide'}

villages = aggregate(a01~vcode_n, data=a_male_2011, FUN = length) #318 villages
upazilla = aggregate(a01~uzcode, data=a_male_2011, FUN = length) #279 upazilla


#calculate household level weekly food expenditure
foodexp_2011 = left_join(o1_female_2011,a_male_2011,by="a01")%>%
  dplyr::select(a01,contains("o1"),vcode_n,dcode)%>%
  mutate(o1_07a=if_else(o1_04 %in% c(1,2,3),o1_08/o1_06,o1_08/o1_05)) #category 1 is kg, cat 2 is g, 3 is liter, and now 4 is g
  #mutate(o1_06a=if_else(o1_04==2,o1_06/1000,o1_06), #change grams into kilos 
        # o1_07a=if_else(o1_04==4,(o1_08/o1_05)/1000,o1_07))%>% #alternate unit price=total val/number of kg reported

  
missing_exp=foodexp_2011%>%
  filter(is.na(o1_07a))

#calculate village level prices: unit mean and unit median prices if there are more than 3 observations in the village for the food item
# prices_village = o1_f_2011_hh%>%
#   dplyr::select(vcode_n,dcode,o1_01,o1_04,o1_06,o1_07,o1_08)%>%
#   arrange(dcode,vcode_n,o1_01,o1_04,o1_07)%>%
#   group_by(o1_01,vcode_n) %>%
#   filter(!is.na(o1_07))%>%
#   dplyr::summarise(unitprice=ifelse(n()>3,mean(o1_07),0),medprice=ifelse(n()>3,median(o1_08/o1_06),0))%>%
#   dplyr::na_if(0) #convert zero to NA

prices=foodexp_2011%>%
  dplyr::select(o1_01,o1_04,o1_06,o1_07,o1_07a,o1_08)%>%
  #arrange(o1_01,o1_04)%>%
  group_by(o1_01,o1_04) %>%
dplyr::summarise(mp=median(o1_07a,na.rm=TRUE))

  # filter(!is.na(o1_07))%>%
  # dplyr::summarise(unitprice=ifelse(n()>3,mean(o1_07),0),medprice=ifelse(n()>3,median(o1_08/o1_06),0))%>%
  # dplyr::na_if(0) #convert zero to NA

#join food expenditures with village food prices
foodexp_2011 = left_join(foodexp_2011,prices,by=c("o1_01","o1_04"))%>%
  mutate(foodprod=mp*o1_10,foodother=mp*o1_11) %>%
 dplyr::na_if(0) #convert zero to NA
  
foodexp_2011_hh = foodexp_2011%>%
  group_by(a01) %>%
  dplyr::summarise(foodpurch_hhwk=sum(o1_08,na.rm=TRUE),foodprod_hhwk=sum(foodprod,na.rm=TRUE),
            foodother_hhwk=sum(foodother,na.rm=TRUE))%>%
  mutate(foodtot_hhwk=rowSums(.[2:3],na.rm=TRUE)) #only include purch and prod


#calculate household level weekly nonfood expenditure from monthly
nonfoodexp_2011_m = p1_male_2011 %>%
  group_by(a01) %>%
  dplyr::summarise(p1_02=sum(p1_02,na.rm=TRUE),p1_04=sum(p1_04,na.rm=TRUE)) %>%
  mutate(nonfoodexp1_hhwk=(p1_02+p1_04)*12/52) 

#calculate household level weekly nonfood expenditure from annual
nonfoodexp_2011_y = p2_male_2011 %>%
  group_by(a01) %>%
  dplyr::summarise(p2_03=sum(p2_03,na.rm=TRUE),p2_06=sum(p2_06,na.rm=TRUE)) %>%
  mutate(nonfoodexp2_hhwk=(p2_03+p2_06)/52)    

#combine all nonfood exp expenditures
nonfoodexp_2011_hh=left_join(nonfoodexp_2011_m,nonfoodexp_2011_y,by="a01") %>%
  mutate(nonfoodexp_hhwk=nonfoodexp1_hhwk + nonfoodexp2_hhwk) %>%
  dplyr::select(a01,nonfoodexp_hhwk)



#add food expenditures to household roster_2011
roster_2011_hh=left_join(roster_2011_hh,nonfoodexp_2011_hh,by=c("hhid"="a01")) %>%
  mutate(nonfoodexp_hhwk_pc=nonfoodexp_hhwk/hhsize,
         nonfoodexp_hhwk_AE_OECD=nonfoodexp_hhwk/AE_OECD)%>%
left_join(foodexp_2011_hh,by=c("hhid"="a01")) %>%
  mutate(foodpurch_hhwk_pc = foodpurch_hhwk/hhsize,
    foodpurch_hhwk_AE_OECD = foodpurch_hhwk/AE_OECD,
    foodtot_hhwk_pc = foodtot_hhwk/hhsize,
    foodtot_hhwk_AE_OECD = foodtot_hhwk/AE_OECD)%>%
  mutate(foodshare=if_else(nonfoodexp_hhwk>0 & foodtot_hhwk>0,foodtot_hhwk/(foodtot_hhwk+nonfoodexp_hhwk),0))

#dplyr::na_if(roster_2011_hh$foodshare,0) #convert zero to NA

rm(nonfoodexp_m_hh,nonfoodexp_y_hh,upazilla,villages,prices,foodexp_2011,foodexp_2011_hh,nonfoodexp_2011_hh,nonfoodexp_2011_m,nonfoodexp_2011_y,missing_exp)

```

9. Food Security measures (hdds tbd)
```{r food security, echo=FALSE}

foodsecurity=x3_female_2011%>%
  dplyr::rename(hhid=a01,nofood_freq=x3_02,hungrynight_freq=x3_04,hungryday_freq=x3_06)%>%
  mutate(nofood=if_else(x3_01==1,1,0),hungrynight=if_else(x3_03==1,1,0),hungryday=if_else(x3_05==1,1,0))%>%
  dplyr::select(hhid,contains("no"),contains("hungry"))

# #need to finish HDDS %>%
#   mutate(cereal=if_else(x3_07_1>0|x3_07_2>0|x3_07_4>0,1,0),
#          tubers=if_else(x3_07_3==1,1,0),
#          vegetables=if_else(x3_07_5==1,1,0),
#          fruits=if_else(x3_07_6==1,1,0),
#          meat=if_else(x3_07_10==1|x3_07_11==1,1,0),
#          eggs=if_else(x3_07_8==1,1,0),
#          seafood=if_else(x3_07_12==1,1,0),
#          pulses=if_else(x3_07_7==1|x3_07_16==1,1,0),
#          milk=if_else(x3_07_9==1,1,0),
#          fats=if_else(x3_07_13==1,1,0),
#          sugar=if_else(x3_07_14==1,1,0),
#          misc=if_else(x3_07_15==1|x3_07_17==1,1,0))%>%
#   mutate(hdds=)
  
#add back to HH level roster
roster_2011_hh=left_join(roster_2011_hh,foodsecurity,by="hhid")


rm(foodsecurity)

```



(tbd) Assistance Type
```{r assistance, echo=FALSE}
#breakdown of assistance type (for all households)
# assistance = u_male_2011 %>%
#   filter(u01==1) 
# 
# assistance_count = aggregate(a01~slno, data=assistance, FUN = length)

# %>%
#   group_by(a01)%>%
#   summarise(u01_hh=n(mid_1)+n(mid_2))
```

Clean up global environment
```{r}

rm(list=ls(pattern="male")) 
   
```



Descriptives
D1. Summary of unweighted sample (6503 HH)
```{r total sample, echo=FALSE}

### SUMMARY of all 6503 households (ie: 15 hh dropped with two spouses)
roster_2011_hh.summary = roster_2011_hh %>%
    psych::describe() %>%
  as_tibble(rownames="rowname") %>%
  dplyr::select(rowname,n,mean,sd)

#print(roster_2011_hh.summary,digits=3)

```


D2. Add survey weights and restrict to representative sample (5503 HH)
```{r summary, echo=FALSE}
sample_type = aggregate(hhid~sampletype, data=roster_2011_hh, FUN = length)
#1:FTF Original 1000
#2:FTF Additional 1080
#3:National Representative 4423

#import weights
weights_2011 <- read_dta("C:/Users/lilac2/Box/BIHS Project/Data/Raw Data/bihs_2011_2012/IFPRI_BIHS_R1_expenditure.dta") %>%
  dplyr::select(a01,dvcode,vcode,aeu,hhweightR1,popweightR1)

#weights_2015 <- read_dta("C:/Users/lilac2/Box/BIHS Project/Data/Raw Data/bihs_2015/IFPRI_BIHS_R2_exp.dta")

wroster_2011_hh=left_join(roster_2011_hh,weights_2011,by=c("hhid"="a01"))%>%
  filter(sampletype==2 |sampletype==3)%>%
  filter(poly==0)

wroster_2011_I=left_join(roster_2011_I,weights_2011,by=c("hhid"="a01"))%>%
  filter(sampletype==2 |sampletype==3)%>%
  filter(I_kcal>0 & mealdata>0&poly==0 & age>=1)


wroster_2011_hh.summary = wroster_2011_hh %>%
    psych::describe() %>%
  as_tibble(rownames="rowname") %>%
  dplyr::select(rowname,n,mean,sd)


rm(sample_type)

```



Import AE and Nutrient Requirements
```{r nutrient requirements}

setwd("C:/Users/lilac2/Box/BIHS Project/Data")

wroster_2011_I=left_join(roster_2011_I,weights_2011,by=c("hhid"="a01"))%>%
  filter(sampletype==2 |sampletype==3)%>%
  filter(I_kcal>0 & mealdata>0 & poly==0 & age>=1 & abroad==2)%>%
  dplyr::select(-abroad,-poly,-mealdata)

#INDIA requirements and AE
#read in D&T's version of adult equivalent from India
AE_India <- read_excel("./Clean Data/GuidelinesIndia_2011.xlsx",sheet="AE_India",range = "A1:D13",col_types =  "numeric")


#join AE
wroster_2011_I=fuzzy_left_join(wroster_2011_I,AE_India, 
                by=c("age"="agemin", "age"="agemax"),
                match_fun=list(`>=`, `<=`))%>%
  mutate(AE_India=if_else(sex==1,AE_male,AE_female))%>%
  dplyr::select(-(38:41))


#India Dietary requirements
India_RDA<-read_excel("./Clean Data/GuidelinesIndia_2011.xlsx",sheet="India_RDA",range = "A1:k19",col_names = TRUE)%>%
  mutate(sex=if_else(sex=="male",1,2),agemin=as.numeric(agemin),agemax=as.numeric(agemax),
         activity=if_else(is.na(activity),"light",activity))%>%
  dplyr::select(-1)


#join India requirements
wroster_2011_I=wroster_2011_I%>%
  mutate(activityI=if_else(age>=18,activity,"light"))%>%
  fuzzy_left_join(India_RDA,
                by=c("sex","activityI"="activity","age"="agemin", "age"="agemax"),
                match_fun=list(`==`,`==`,`>=`, `<=`))%>%
   dplyr::rename(activity=activity.x,sex=sex.x,refwt_India=weight_kg)%>%
  mutate(range_India=if_else(!is.na(agemin),paste(as.character(agemin),as.character(agemax),sep="-"),as.character(NA)),
    kcal_India=if_else(pregnant==1,kcal_India+250,if_else(lactating==1,kcal_India+560,kcal_India)),
         protein_India=if_else(pregnant==1,protein_India+23,if_else(lactating==1,protein_India+16,protein_India)))%>%
  dplyr::select(-contains(".y"),-agemin,-agemax)



#FAO requirements and AE
FAO_adult <- read_excel("./Clean Data/FAO_energyrequirements_2011.xlsx",sheet="Adult_BMRPAL",range = "A1:N19",col_names = TRUE)%>% 
 dplyr::select(1:3,7,8,10,12,13,14)%>% 
  mutate(sex=if_else(sex=="Male",1,2))

FAO_child <- read_excel("./Clean Data/FAO_energyrequirements_2011.xlsx",sheet="Child_TEEPAL",range = "A1:M25",col_names = TRUE)%>% 
 dplyr::select(1:3,7,8,10,12,13)%>% 
  mutate(sex=if_else(sex=="Male",1,2))

FAO=bind_rows(FAO_adult,FAO_child)

#nutrition subset for individuals
#calculate BMR and FAO daily energy requirement=BMR x PAL, add 285 kcal/d for pregnancy, and 500 kcal/day if breastfeeding
wroster_2011_I=wroster_2011_I%>%
 mutate(sex=as.numeric(sex))%>%
  fuzzy_left_join(FAO,by=c("sex","activity","age"="agemin","age"="agemax"),match_fun=list(`==`,`==`,`>=`,`<`))%>%
dplyr::rename(sex=sex.x,activity=activity.x,AE_FAO=AME_FAO)%>%
mutate(range_FAO=if_else(!is.na(agemin),paste(as.character(agemin),as.character(agemax),sep="-"),as.character(NA)),
       kcal_FAO=if_else(pregnant==1,EER+285,if_else(lactating==1,EER+485,EER)))%>%
  dplyr::select(-contains(".y"),-EER,-agemin,-agemax)


rm(list=ls(pattern="FAO"))
rm(list=ls(pattern="India"))

library(plyr)

#DRI standards from Schenider/Hertforth
DRI_standards = read_dta("C:/Users/lilac2/Box/BIHS Project/Programs/Stata/EAR+UL+AMDR+CDDR_allgroups.dta")%>%
# mutate(sex=if_else(age_sex_grp%in%c(4,6,8:13),1,if_else(age_sex_grp%in%c(5,7,14:25),2,as.numeric(NA))),
#          agegrp_who=if_else(lifestage==4,"infant",if_else(lifestage==3,"child",if_else(lifestage==1,"adolescent",if_else(lifestage==2,"adult",
#                              if_else(lifestage==6,"senior",if_else(lifestage==5,"lactating",if_else(lifestage==7,"pregnant",as.character(NA)))))))))%>%
  filter(nutr_no %in%c(2,3,4,5,16,18)&age_sex_grp>2&!is.na(sex))%>%
dplyr::mutate(sex=if_else(sex==0,1,2),activity=if_else(pal==1,"light",if_else(pal%in%c(2,3),"moderate",if_else(pal==4,"heavy",as.character(NA)))),
  pregnant=if_else(lifestage==7,1,0),lactating=if_else(lifestage==5,1,0),
              nutr=revalue(nutr,c("Energy"="kcal","Carbohydrate"="carb","Protein"="protein","Lipids"="fat","Calcium"="calcium","Iron"="iron")))%>%
dplyr::rename(agemin=age_lower_yrs,agemax=age_upper_yrs)%>%
  mutate(agemin=if_else(agemax==3,2,agemin))%>%
 mutate(agemin=if_else(lifestage==6,70,agemin),agemax=if_else(lifestage==6,150,agemax))%>%
  dplyr::select(3,4,6,7,10,11,15:18)%>%
  group_by(sex,agemin,agemax,activity,pregnant,lactating,nutr)%>%
  dplyr::summarise_all(mean)

calc_iron=DRI_standards%>%
  filter(nutr%in%c("calcium","iron"))
  
activity2=c("light","moderate","heavy")  
new=expand_grid(calc_iron,activity2)%>%
  dplyr::select(1:3,11,5:10)%>%
  dplyr::rename(activity=activity2)

DRI_standards=DRI_standards%>%
  filter(!nutr%in%c("calcium","iron"))

DRI_standards=bind_rows(DRI_standards,new)

base_iom=DRI_standards%>%
  filter(sex==1&agemin==19&activity=="moderate"&nutr=="kcal")
x=base_iom$ear

DRI=DRI_standards%>%
  gather(standard,nutr_value,8:10)%>%
  filter(!is.na(nutr_value))%>%
  unite(nutr,standard,col="nutr_standard",sep="_")%>%
  dplyr::select(sex,agemin,agemax,activity,pregnant,lactating,nutr_standard,nutr_value)%>%
  spread(nutr_standard,nutr_value)%>%
  dplyr::rename(calcium_IOM=calcium_ear,iron_IOM=iron_ear,protein_IOM=protein_ear,kcal_IOM=kcal_ear)%>%
  mutate(AE_IOM=kcal_IOM/x)


#join DRI standards with roster
wroster_2011_I=wroster_2011_I%>%
fuzzy_left_join(DRI,by=c("sex","age"="agemin", "age"="agemax","activityI"="activity","pregnant","lactating"),match_fun=list(`==`,`>=`, `<=`,`==`,`==`,`==`))%>%
dplyr::rename(sex=sex.x,activity=activity.x,pregnant=pregnant.x,lactating=lactating.x)%>%
mutate(range_IOM=if_else(!is.na(agemin),paste(as.character(agemin),as.character(agemax),sep="-"),as.character(NA)))%>%
  dplyr::select(-contains(".y"),-agemin,-agemax)



#add back HH-level variables and generate three more hh level
hh=wroster_2011_I%>%
  group_by(hhid)%>%
  dplyr::summarise(hhsize_India=sum(AE_India,na.rm=TRUE),hhsize_FAO=sum(AE_FAO,na.rm=TRUE),hhsize_IOM=sum(AE_IOM,na.rm=TRUE))

wroster_2011_hh=left_join(wroster_2011_hh,hh,by="hhid")

h=wroster_2011_hh%>%
  dplyr::select(hhid,contains("hhsize_"),contains("hh_"),AE_OECD)%>%
  dplyr::rename(hhsize_OECD=AE_OECD)

wroster_2011_I=left_join(wroster_2011_I,h,by="hhid")%>%
  mutate(share_India=AE_India/hhsize_India,share_FAO=AE_FAO/hhsize_FAO,share_IOM=AE_IOM/hhsize_IOM)


rm(DRI_standards,calc_iron,activity2,new,h,hh,base_iom,x)

# DRI_split=split(DRI_standards,DRI_standards$nutr)
# DRI_names=names(DRI_split)
# for (i in 1:length(DRI_names)) {
#   y=DRI_split[[i]]
#   assign(paste("DRI",DRI_names[i],sep="_"), y)
#   x=wroster_2011_I%>%dplyr::select(1:6,8:16,24,25,36:43,49:52,54,contains(DRI_names[i]))%>%
#     fuzzy_left_join(y,by=c("age"="agemin", "age"="agemax","sex","activityI"="activity","pregnant","lactating"),match_fun=list(`>=`, `<=`,`==`,`==`,`==`,`==`))%>%
#     dplyr::rename(sex=sex.x,activity=activity.x)%>%
#     dplyr::select(-lifestage,-contains(".y"),-agemin,-agemax,-nutr)
#   assign(paste(DRI_names[i],"nutrition",sep="_"),x)
# }

#rm(list=ls(pattern="DRI"),x,y)


```


Summary Table for D&T
```{r DT, echo=FALSE}

## SUMMARY TABLES FOR D&T SUBSET
# "we restrict the sample to households with male, married heads whose spouses are present and to
# households without pregnant or lactating women. This sample of 3,060 house-holds..." (page 631)

##DST TABLE 1
roster_hh_DST = wroster_2011_hh %>%
  filter(sexhead==1 & maritalhead==2 & abroadhead==0 & poly==0 & porl_hh==0 & spouseabroad_hh==0) 

#nrow(filter(roster_hh_DST,is.na(BMIhead))) #86 missing
#nrow(filter(roster_hh_DST,is.na(BMIspouse))) #45 missing

design_hh_DT <- svydesign(data=roster_hh_DST,id=~vcode, strata=~dvcode,weights=~hhweightR1)

listx = dplyr::select(roster_hh_DST,22,53,63,66,2,19,20,6,7,8,33,37:42,43,46:51)
a=svymean(listx,design_hh_DT,na.rm=TRUE)
print(ftable(a),digits=2)

#this is not weighted, use svymean for weighted results
roster_hh_DST.summary = roster_hh_DST %>%
  psych::describe() %>%
  as_tibble(rownames="rowname") %>%
  dplyr::select(rowname,n,mean,sd)

#print(roster_hh_DST.summary,digits=3)
# 
# table1= dplyr::bind_cols(roster_2011_hh.summary,roster_hh_DST.summary) %>%
#   dplyr::select(-rowname1)%>%
#   dplyr::rename(obs_full=n,mean_full=mean,sd_full=sd,obs_sample=n1,mean_sample=mean1,sd_sample=sd1) %>%
#   dplyr::filter(rowname=="hhdaycalperAE" |rowname=="hhdayecalperAE" | rowname=="nonfoodexp_hhwkpc" | rowname=="foodpurch_hhwkpc" | rowname=="foodshare" | rowname=="hhsize" | rowname=="AE" | rowname=="boy" | rowname=="girl" | rowname=="otheradult"
#                 | rowname=="agehead" |rowname=="lithead" |rowname=="noschoolhead" |rowname=="secondschoolhead" |rowname=="agworkhead" |rowname=="BMIhead"
#                 | rowname=="agespouse" |rowname=="litspouse" |rowname=="noschoolspouse" |rowname=="secondschoolspouse" |rowname=="agworkspouse" |rowname=="BMIspouse") 
# 
# 
# kable(table1,booktabs=TRUE,digits=2,caption="Table 1", col.names=c("Variable","N","Mean","SD","N","Mean","SD"),align='r')%>%
#   kable_styling(full_width=TRUE)%>%
#   pack_rows("Household Head",8,13)%>%
#   pack_rows("Spouse",14,19)%>%
#   pack_rows("Expenditures",20,22)%>%
#   add_header_above(c(" "=1,"All Households"=3,"D&T Sample"=3))
# 

###TABLE 3
roster_I_DST=wroster_2011_I%>%
  filter(sexhead==1 & maritalhead==2 & abroadhead==0 & poly==0 & porl_hh==0 & spouseabroad_hh==0)%>%
  mutate(BMIunder=if_else(BMI<18.5,(18.5-BMI)/18.5,0),
         adultgrp=if_else(relation==1,"head",if_else(relation==2,"spouse",if_else(otheradult==1,"otheradult",as.character(NA)))))%>%
   filter(!is.na(agegrp_DST),!is.na(BMI),!is.na(adultgrp))%>%
  dplyr::select(hhid,mid,agegrp_DST,adultgrp,BMI,BMIunder,vcode,dvcode,popweightR1)

#%>%
 # reshape2::cast(agegrp~adultgrp,fun.aggregate=c(mean,sd,n))

#roster_I_DST$DST[is.na(roster_I_DST$DST)]<-0 #convert zero to NA
design_I_DT <- svydesign(data=roster_I_DST,id=~vcode, strata=~dvcode,weights=~popweightR1)

table3= roster_I_DST %>%
  group_by(agegrp_DST,adultgrp) %>%
  summarise(mean=mean(BMIunder),se=sd(BMIunder)/sqrt(length(BMIunder)),n=n())%>%
  reshape2::melt(id.vars=c("agegrp_DST","adultgrp"),measure.var=c("mean","se","n"))%>%
  dplyr::arrange(agegrp_DST)%>%
  unite(agegrp_DST,variable,col="agegrp_DST_var",sep="_")%>%
  dcast(agegrp_DST_var~adultgrp,value.var = "value")%>%
  separate(agegrp_DST_var,into=c("agegrp_DST","var"),"_")%>%
  dplyr::select(var,head,spouse,otheradult)
# 
# 
# kable(table3,booktabs=TRUE,digits=3,caption="Table 3: BMI Shortfalls", col.names=c("","Heads","Spouses","Other Adults"),align='r')%>%
#   kable_styling(full_width=TRUE)%>%
#   pack_rows("Ages 20-39",1,3)%>%
#   pack_rows("Ages 40-59",4,6)%>%
#   pack_rows("Ages 60 and up",7,9)

#%>%
 # add_header_above(c(" "=1,"All Households"=3,"D&T Sample"=3))


```


METHODOLOGY
Nutrient = calories, fat, protein, carb, calcium,iron
1. Individual consumption of nutrients (Six variables labeled "I_nutrient")
2. BMI (one variable labeled "BMI")
3. HDDS (not yet done)

Calculated measure = Total household consumption of nutrient/measure of household size

Variation in Denominator:
a.	HH size (PC)
b.	OECD adult equivalent 
c.	AE based on age group and gender
d.  AE accounting for pregnancy/lactation
e.	AE based on age
f.	Add on activity as defined by employment category 
g.	Add on activity as defined by time use
h.	AE using height and weight 
i.	Adult Male Equivalent (is this different than AE?) 
j.	AE benchmarks from Bangladesh./India
k.	AE benchmarks from FAO
l.	AE benchmarks from USDA



12. Individual inadequacy by comparing actual consumption to target
```{r I_indequality}

setwd("C:/Users/lilac2/Box/BIHS Project/Programs/R/output")

for (i in 1:length(nutnames)) {
  temp=wroster_2011_I%>%
    dplyr::select(1:15,23,33:37,39,contains("range"),contains("share"),hhsize,hhsize_OECD,contains(nutnames[[i]]))

   assign(paste(nutnames[[i]],"inadequacy",sep="_"),temp)
}


#for (x in nutnames){
# temp[[paste("Ishare_India",i,sep="_")]]<-temp
 # wroster_2011_I_LC[[paste(x,"gap_PC_I",sep="_")]]<-(wroster_2011_I_LC[[paste("hh_",x,"_PC")]] - wroster_2011_I_LC[[x]]) / wroster_2011_I_LC[[paste("hh_",x,"_PC")]]
#}

design_I <- svydesign(data=wroster_2011_I,id=~vcode, strata=~dvcode,weights=~popweightR1)

#India standards
India_inadequacy=wroster_2011_I%>%
  dplyr::select(1:23,33:39,contains("India"))%>%
  mutate(kcal_inadequate=if_else(I_kcal<kcal_India,1,0),
         protein_inadequate=if_else(I_protein<protein_India,1,0),
         fat_inadequate=if_else(I_fat<fat_India,1,0),
         calcium_inadequate=if_else(I_calcium<calcium_India,1,0),
         iron_inadequate=if_else(I_iron<iron_India,1,0))%>%
   mutate(kcal_gap_India=if_else(kcal_inadequate==1,(I_kcal-kcal_India)/kcal_India,as.numeric(NA)),
         protein_gap_India=if_else(protein_inadequate==1,(I_protein-protein_India)/protein_India,as.numeric(NA)),
         fat_gap_India=if_else(fat_inadequate==1,(I_fat-fat_India)/fat_India,as.numeric(NA)),
         calcium_gap_India=if_else(calcium_inadequate==1,(I_calcium-calcium_India)/calcium_India,as.numeric(NA)),
         iron_gap_India=if_else(iron_inadequate==1,(I_iron-iron_India)/iron_India,as.numeric(NA)))%>%
  dplyr::select(vcode,dvcode,popweightR1,sex,range_India,contains("kcal"),contains("protein"),contains("fat"),contains("calcium"),contains("iron"))

India_w=India_inadequacy%>%
  as_survey_design(ids=vcode, strata=dvcode,weights=popweightR1)%>%
  group_by(sex,range_India)%>%
  summarise_all(survey_mean,na.rm=TRUE)%>%
  dplyr::select(-(3:8),-contains("_se"))

age=c("1-3","4-6","7-9","10-12","13-15","16-17","18-120")
India_w$range_India<-reorder.factor(India_w$range_India,new.order=age)

India_w=India_w%>%
  arrange(range_India)%>%
mutate_at(vars(contains("gap")),funs(scales::percent(.,accuracy=.1)))%>%
mutate_at(vars(contains("inadequate")),funs(scales::percent(.,accuracy=.1)))%>%
  mutate_at(vars(contains("I_")),funs(round(.,2)))

          
          
India_print<-kable(India_w,booktabs=TRUE,caption="Individual Nutrient Inadequacy using India Standards",
      col.names=c("Sex","Age Range",
            "Actual Individual Consumption","Requirement","Inadequacy Frequency","Inadequacy Severity",
            "Actual Individual Consumption","Requirement","Inadequacy Frequency","Inadequacy Severity",
            "Actual Individual Consumption","Requirement","Inadequacy Frequency","Inadequacy Severity",
            "Actual Individual Consumption","Requirement","Inadequacy Frequency","Inadequacy Severity",
            "Actual Individual Consumption","Requirement","Inadequacy Frequency","Inadequacy Severity"),
      escape=F)%>%
  kable_styling(full_width=TRUE)%>%     
add_header_above(c(" "=2,"Energy (kcal/day)"=4, "Protein (g/day)"=4,"Fat (g/day)"=4, "Calcium (mg/day)"=4,
                   "Iron (mg/day)"=4)) %>% 
   column_spec(c(2,6,10,14,18),border_right = TRUE)%>%
  row_spec(c(1,14),hline_after= T)%>%
 footnote(general="Inadequacy Frequency is Proportion of Sex/Age group that consumed below the requirement. Inadequacy Severity is the percent of below the requirement of the average intake. Means are weighted using IFPRI sample weights.")

save_kable(India_print,"India_inadequacy.png")
print(India_print)


#FAO standards
FAO_inadequacy=wroster_2011_I%>%
  dplyr::select(1:23,33:39,contains("FAO"))%>%
   mutate(kcal_inadequate=if_else(I_kcal<kcal_FAO,1,0),
         protein_inadequate=if_else(I_protein<protein_FAO,1,0))%>%
  mutate(kcal_gap_FAO=if_else(kcal_inadequate==1,(I_kcal-kcal_FAO)/kcal_FAO,as.numeric(NA)),
         protein_gap_FAO=if_else(protein_inadequate==1,(I_protein-protein_FAO)/protein_FAO,as.numeric(NA)))%>%
  dplyr::select(vcode,dvcode,popweightR1,sex,range_FAO,contains("kcal"),contains("protein"))

FAO_w=FAO_inadequacy%>%
  as_survey_design(ids=vcode, strata=dvcode,weights=popweightR1)%>%
  group_by(sex,range_FAO)%>%
  summarise_all(survey_mean,na.rm=TRUE)%>%
  dplyr::select(-(3:8),-contains("_se"))

age=c("1-4","4-9","9-14","14-18","18-30","30-60","60-150")
FAO_w$range_FAO<-reorder.factor(FAO_w$range_FAO,new.order=age)

FAO_w=FAO_w%>%
  arrange(range_FAO)%>%
mutate_at(vars(contains("gap")),funs(scales::percent(.,accuracy=.1)))%>%
mutate_at(vars(contains("inadequate")),funs(scales::percent(.,accuracy=.1)))%>%
  mutate_at(vars(c("kcal_FAO",contains("I_"))),funs(round(.,2)))%>%
  filter(!is.na(range_FAO))%>%
  mutate_at(vars(c("protein_inadequate","protein_gap_FAO")),funs(revalue(.,c("0.0%"=as.character(NA)))))%>%
mutate(protein_FAO=if_else(protein_FAO==0,as.numeric(NA),round(protein_FAO,2)))

          
FAO_print<-kable(FAO_w,booktabs=TRUE,caption="Individual Nutrient Inadequacy using FAO/WHO Standards",
      col.names=c("Sex","Age Range",
            "Actual Individual Consumption","Requirement","Inadequacy Frequency","Inadequacy Severity",
            "Actual Individual Consumption","Requirement","Inadequacy Frequency","Inadequacy Severity"),
      escape=F)%>%
  kable_styling(full_width=TRUE)%>%     
add_header_above(c(" "=2,"Energy (kcal/day)"=4, "Protein (g/day)"=4))%>% 
   column_spec(c(2,6,10),border_right = TRUE)%>%
  row_spec(c(1,14),hline_after= T)%>%
 footnote(general="Inadequacy Frequency is Proportion of Sex/Age group that consumed below the requirement. Inadequacy Severity is the percent of below the requirement of the average intake. Means are weighted using IFPRI sample weights.")


save_kable(FAO_print,"FAO_inadequacy.png")
print(FAO_print)




#IOM standards
IOM_inadequacy=wroster_2011_I%>%
  dplyr::select(1:23,33:39,contains("IOM"),contains("amdr"))%>%
   mutate(kcal_inadequate=if_else(I_kcal<kcal_IOM,1,0),
         protein_inadequate=if_else(I_protein<protein_amdr_lower,1,0),
          carb_inadequate=if_else(I_carb<carb_amdr_lower,1,0),
         fat_inadequate=if_else(I_fat<fat_amdr_lower,1,0),
         calcium_inadequate=if_else(I_calcium<calcium_IOM,1,0),
         iron_inadequate=if_else(I_iron<iron_IOM,1,0))%>%
  mutate(kcal_gap_IOM=if_else(kcal_inadequate==1,(I_kcal-kcal_IOM)/kcal_IOM,as.numeric(NA)),
         calcium_gap_IOM=if_else(calcium_inadequate==1,(I_calcium-calcium_IOM)/calcium_IOM,as.numeric(NA)),
         iron_gap_IOM=if_else(iron_inadequate==1,(I_iron-iron_IOM)/iron_IOM,as.numeric(NA)),
         protein_gap_IOM=if_else(protein_inadequate==1,(I_protein-protein_amdr_lower)/protein_amdr_lower,as.numeric(NA)),
         carb_gap_IOM=if_else(carb_inadequate==1,(I_carb-carb_amdr_lower)/carb_amdr_lower,as.numeric(NA)),
         fat_gap_IOM=if_else(fat_inadequate==1,(I_fat-fat_amdr_lower)/fat_amdr_lower,as.numeric(NA)))%>%
 dplyr::select(sex,range_IOM,contains("kcal"),contains("protein"),contains("carb"),contains("fat"),contains("calcium"),contains("iron"),-contains("upper"),-protein_IOM)%>%
  group_by(sex,range_IOM)%>%
  dplyr::summarise_all(mean,na.rm=TRUE)%>%
filter(!is.na(range_IOM))











```



