---
title: "BIHS_2015_coding"
author: "Lila Cardell"
date: "September 28, 2021"
output: html_document
#fontsize: 11pt
---

Set working directory and install packages
```{r setup, echo=FALSE,warning=FALSE,message=FALSE,results='hide'}

knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = FALSE,
	root.dir = 'C:/Users/lilac2/Box/BIHS_Project'
)
knitr::opts_knit$set(root.dir='C:/Users/lilac2/Box/BIHS_Project')

options(scipen=999)
set.seed(12345)


## Clear worksace
rm(list = ls())
gc()


## This function will check if a package is installed, and if not, install it
pkgTest  =  function(x) {
  if (!require(x, character.only = TRUE))
  {
    install.packages(x, dep = TRUE)
    if(!require(x, character.only = TRUE)) stop("Package not found")
  }
}

## These lines load the required packages
packages  =  c('plyr','data.table','tidyverse','haven','stargazer','plm','lubridate','survey','psych','knitr','xtable','tables','kableExtra','fuzzyjoin','MASS','matrixcalc','car','stringr','styler','readxl','magrittr','sjmisc','readxl','srvyr','gdata','labelled')


lapply(packages, pkgTest)




```



1. Import BIHS data
```{r import BIHS,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}
# Read in data for project


#this pulls in all 2015 household level files except the WEAI
filenames<-grep(list.files(path="./Data/Raw Data/bihs_2015/household/data"),pattern=c("weai","h"),inv=TRUE,value=TRUE)
names<-gsub(".dta","",filenames)

 for(i in names){
   filepath <- file.path(paste("./Data/Raw Data/bihs_2015/household/data/",i,".dta",sep=""))
   if (i == "003_r2_male_mod_b1") {
     assign(paste("b1_male_2015"),haven::read_dta(filepath))
   }
   assign(paste(substring(i,12),"_2015",sep=""),haven::read_dta(filepath))
 }



#read in the 2015 census and 2015 consumption file for now
#census_2015 = read_dta("./Raw Data/bihs_2015_2012/census/data/001_census_ftf.dta")




#import names of menu items from the 2015 codebook
#this is assumed to be more comprehensize than 2015 and also available in excel
menucodes = read_excel("./Data/Raw Data/bihs_2015/household/documents/000_codebook.xls", 
                       sheet = "064_r2_mod_x1_1_female", range = "C31:D415",col_names = c("menuname","menu"))


#combine two x1 objects
x1_female_2015 = x1_1_female_2015 %>% 
                  dplyr::rename(menu = x1_05)%>% 
                  select(1:41)
x1_female_2015_2 = x1_2_female_2015 %>% dplyr::rename(menu = x1_05)

x1_female_2015 = rbind(x1_female_2015, x1_female_2015_2)

#count menu items
menu_items = aggregate(a01~menu, data=x1_female_2015, FUN = length)%>%
  left_join(menucodes,by=c("menu"))%>%
dplyr::rename("menucode"="menu","hh_num" = "a01")%>%
  arrange(desc(hh_num))
#206 items consumed in 2015
#issue with salt not being separated into iodine/non-iodine in 2015
#menu_items = aggregate(a01~x1_05, data=x1_1_f_2015, FUN = length) #180 items consumed in 2015
#1/3 salt is regular, 2/3 iodine (return to this later)


###import names of ingredient items from 2015 (assumed to be more comprehensize than 2015)
ingredientcodes = read_excel("./Data/Raw Data/bihs_2015/household/documents/000_codebook.xls", 
                             sheet = "064_r2_mod_x1_1_female", range = "C417:D717", col_names =c("ingredientname","ingredient"))%>%
 add_row(ingredientname="Salt",ingredient=252)

occupationcodes=read_excel("./Data/Raw Data/bihs_2015/household/documents/000_codebook.xls", 
                             sheet ="003_r2_male_mod_b1", range = "C106:D182", col_names = c("occupation_name","occupation_code"))




rm(filenames,filepath,i,names)

```



2. Import FCT Data
```{r import FCT,echo=FALSE,warning=FALSE,message=FALSE,results='hide'}


###Import nutrition data
FCT_Bangladesh =read_excel("./Data/Clean Data/nutrient tables/FCDB_7_4_14_LC.xlsx",sheet = "UserDB_Main_table")%>% 
dplyr::select(2,3,8,11:13,16,17)%>% 
 dplyr::rename(name=2,kcal=3,protein=4,fat=5,carb=6,calcium=7,iron=8)%>%
  filter(!is.na(BIHS_code))%>%
   mutate_at(vars(1,3:8),as.numeric,na.omit=TRUE)


FCT_India=read_excel("./Data/Clean Data/nutrient tables/ifct2017_compositions.xlsx",sheet = "Data")%>% 
  dplyr::select(1,3,enerc,protcnt,fatce,choavldf,ca,fe)%>% 
  dplyr::rename(kj=3,protein=4,fat=5,carb=6,calcium=7,iron=8)%>%
  filter(!is.na(BIHS_code))%>%
   mutate_at(vars(1,3:8),as.numeric,na.omit=TRUE)%>%
  mutate(kcal=kj/4.184)%>%
  dplyr::select(BIHS_code,name,kcal,protein,fat,carb,calcium,iron)

#FCT_B=anti_join(FCT_Bangladesh,FCT_India,by=c("BIHS_code"))%>%
 #  mutate_at(vars(1,3:8),as.numeric,na.omit=TRUE)

FCT_all=bind_rows(FCT_India,FCT_Bangladesh)%>%
  arrange(BIHS_code)%>%
  dplyr::select(-name)%>%
  group_by(BIHS_code)%>%
  dplyr::summarise_all(max)

nutrients = left_join(ingredientcodes,FCT_all,by=c("ingredient"="BIHS_code"))


rm(FCT_Bangladesh,FCT_India,FCT_all)

```


3. Calculate calories for each recipe
```{r calculate recipe calories}


#join recipe dataset with menucodes to include menu names
x1_f_2015_m = left_join(x1_female_2015,menucodes,by=c("menu"))%>%
  mutate(date=as_date(paste(x1_yy, x1_mm, x1_dd,sep="-")))%>%
  dplyr::rename(rid=x1_rid,time=x1_03,menucode=menu,foodsource=x1_02,menucookwt=x1_09)%>%
  dplyr::select("a01","hh_type","rid","date","time","foodsource","menucode","menuname","menucookwt",contains("x1_07"),contains("x1_08"))%>%
  filter(!menucode %in% c(252,2521,2522)) #this is salt

#rename variables with ingredient codes and weights to help with reshaping dataset 
names(x1_f_2015_m)<-gsub("x1_07","icode",names(x1_f_2015_m))
names(x1_f_2015_m)<-gsub("x1_08","iweight",names(x1_f_2015_m))
names(x1_f_2015_m)<-gsub("_0","_",names(x1_f_2015_m))


#reshape the recipe dataset to join it with the nutrient dataset
#edit codes ingredients which have two BIHS codes, but are the same thing

nutnames=names(dplyr::select(nutrients,3:8))



recipes=melt(setDT(x1_f_2015_m),measure.vars=patterns("icode","iweight"),variable.name="inumber",value.name=c("icode","iweight"))%>%
  arrange(a01,date,time,menucode)%>%
  filter(is.finite(icode))%>%
  mutate_at(.vars=vars(contains("code")),.funs=list(~recode(.,"14=10;90=80;93=92;95=94;103=157;107=998;108=157;110=157;112=157;115=157;126=123;185=215;187=186;188=189;193=181;204=179;211=179;212=999;217=222;218=226;227=2287;229=228;233=232;235=213;237=189;238=189;243=242;246=999;247=999;253=999;256=999;257=999;261=260;267=162;269=999;305=3121;310=309;311=3121;314=999;905=998;908=189;902=997;909=213;1323=132;1421=142;1422=142;2521=252;2522=252;2886=2885;2876=2873;2896=2894;2781=278;2782=278;2770=277;2771=277;2772=277;2773=277;2774=277;2775=277;2776=277;2781=278;2782=278;2841=284;2842=284;2843=284;2851=285;2852=285;2861=286;2862=286;2863=286;2871=287;2872=287;2801=280;2802=280;441=44")))%>%
  mutate_at(.vars=vars(contains("code")),.funs=list(~as.numeric(.)))%>%
  left_join(nutrients,by=c("icode"="ingredient"))





#calculate the specific per gram nutrient input of each ingredient: nutrient_c = (ingredient weight in grams x nutrientval per 100g)/100
for (x in nutnames){
 recipes[[paste(x,"c",sep="_")]]<-recipes[[x]]*recipes$iweight/100
}


#investigate ingredients that are missing nutrient info
missing = recipes[is.na(recipes$kcal),]
missing_ingredients = aggregate(a01~icode+ingredientname, data=missing, FUN = length) %>%
  arrange(desc(a01)) # most of these are actually menu items

# #sum nutrients over menu to come up with nutrients per menu item 
# recipe_sum=recipes%>%
#   group_by(a01,hh_type,rid,date,time,foodsource,menucode,menuname,menucookwt)%>%
#  dplyr::summarise_at(vars(iweight,contains("_c")),sum,na.rm=TRUE)%>%
#   dplyr::rename_at(.vars=vars(contains("_c")),.funs=funs(sub("_c","",.)))
# 
#   
# #find the median and 5% and 95% percentile per GRAM nutrient info for each meal
# p <- c(.05,.5,.95)
# p_names <- paste0(p*100, "%")
# p_funs <- map(p, ~partial(quantile, probs = .x, na.rm = TRUE)) %>% 
#   set_names(nm = p_names)
# 
# recipe_med=recipe_sum%>%
#   mutate(across(kcal:iron,~./iweight,na.rm=TRUE))%>%
# filter(kcal>0)%>%
#   group_by(menucode)%>%
# dplyr::summarise(across(kcal:iron,p_funs))
# 
# 
# #resolve missing ingredients that are actually menu items by adding the median per gram nutrient info back into the recipe set and replace missing ingredients with median
# recipes=left_join(recipes,recipe_med,by=c("icode"="menucode"))
# 
# for (x in nutnames){
# recipes[[x]]=if_else(recipes[[x]]==0|is.nan(recipes[[x]])|is.na(recipes[[x]]),recipes[[paste(x,"50%",sep="_")]]*recipes$iweight,
#                                 recipes[[x]])
# }
#     
# 
# #check for missing ingredients again
# missing = recipes[is.na(recipes$kcal),]
# missing_ingredients = aggregate(a01~icode+ingredientname, data=missing, FUN = length) %>%
#   arrange(desc(a01)) #salt and other

#resolve for median per recipe 
#sum nutrients over menu to come up with nutrients per menu item 
recipe_sum=recipes%>%
  group_by(a01,hh_type,rid,date,time,foodsource,menucode,menuname,menucookwt)%>%
 dplyr::summarise_at(vars(iweight,contains("_c")),sum,na.rm=TRUE)%>%
  dplyr::rename_at(.vars=vars(contains("_c")),.funs=funs(sub("_c","",.)))

  
#find the median and 5% and 95% percentile per GRAM nutrient info for each meal
p <- c(.1,.5,.9)
p_names <- paste0(p*100, "%")
p_funs <- map(p, ~partial(quantile, probs = .x, na.rm = TRUE)) %>% 
  set_names(nm = p_names)

recipe_med=recipe_sum%>%
  mutate(across(kcal:iron,~./iweight,na.rm=TRUE))%>%
filter(kcal>0)%>%
  group_by(menucode)%>%
dplyr::summarise(across(kcal:iron,p_funs))

#add the median per gram nutrient info back into the recipe set and replace missing items with median and winsorize at 5%
recipe_hh=left_join(recipe_sum,recipe_med,by=c("menucode"))

for (x in nutnames){
recipe_hh[[x]]=if_else(recipe_hh[[x]]==0|is.nan(recipe_hh[[x]])|is.na(recipe_hh[[x]]),recipe_hh[[paste(x,"50%",sep="_")]]*recipe_hh$iweight,
                       if_else(recipe_hh[[x]]>recipe_hh[[paste(x,"90%",sep="_")]],recipe_hh[[paste(x,"90%",sep="_")]]*recipe_hh$iweight,
                        if_else(recipe_hh[[x]]<recipe_hh[[paste(x,"10%",sep="_")]],recipe_hh[[paste(x,"10%",sep="_")]]*recipe_hh$iweight,
                                recipe_hh[[x]])))
}


recipe_hh=recipe_hh%>%
dplyr::select(1:16)%>%
 dplyr::rename_at(.vars=vars(10:16),.funs=funs(paste("sum",.,sep="_")))



#investigate recipes that are still missing nutrient info
missing = recipe_hh[is.na(recipe_hh$sum_kcal),]
missing_recipes = aggregate(a01~menucode+menuname, data=missing, FUN = length) %>%
  arrange(desc(a01))
#other and burger

rm(recipe_med,recipe_sum,recipes,menucodes,nutrients,missing,x1_female_2015,x1_f_2015_m,x,menu_items,ingredientcodes,missing_ingredients,missing_recipes,p,p_funs,p_names)

```


4. Calculate calories consumed by each individual
```{r calculate individual calories,results='hide'}
#integrate with individual consumption data set and create individual calorie consumption
#there are issues with missing consumption (172 people) and inflated calories counts

# #flag for individuals without consumption data
# datacheck = x2_f_2015  %>%
#   group_by(a01,x2_01) %>%
#   summarise(mealdata = n())%>%
#   filter(x2_01<100)%>%
#   dplyr::rename(mid=x2_01)

#there was a second recall done for 10% of HH, not sure why yet
#x2_1_female_2015 <- x2_1_female_2015 %>% select(!c("sex","age","mem_stat","flag_x2"))
#x2_female_2015 = rbind(x2_1_female_2015, x2_2_female_2015)
#x2_female_2015 <- x2_female_2015[,c(1,3,4,5,6,7,8,9,10,11,12,13,2)]

#join individual reported consumption with recipe nutrition information, and calculate individual nutrient consumption per meal item
recipe_I=x2_1_female_2015%>% 
  dplyr::rename(meal_time=x2_meal,mid=x2_01,mealtaken=x2_03,sex_guest=x2_04,age_guest=x2_05,type_guest=x2_06,menucode=x2_08,icookwt=x2_09,ilocale=x2_11,iorder=x2_12)%>%
  left_join(recipe_hh,by=c("a01","meal_time"="time","menucode"))%>%
  dplyr::mutate(across(sum_kcal:sum_iron,~.*(icookwt/menucookwt),na.rm=TRUE,.names="i_meal{col}"))%>%
  dplyr::select(-hh_type.y,-hh_type.x,-starts_with("sum_"),-menucookwt,-date,-rid,-foodsource,-menuname)

nrow(filter(recipe_I,is.na(i_mealsum_kcal))) #197844 did not match

# #for items that did not match, rematch to see if the time of day reporting was the reason
# recipe_I = left_join(recipe_I,recipe_hh,by=c("a01","menucode"))%>%
#   #dplyr::rename(meal_time=x2_meal,mid=x2_01,mealtaken=x2_03,sex_guest=x2_04,age_guest=x2_05,type_guest=x2_06,menucode=x2_08,icookwt=x2_09,ilocale=x2_11,iorder=x2_12,sample=sample_type.x)%>%
#  dplyr:: mutate(i_mealsum_kcal=if_else(is.na(i_mealsum_kcal),sum_kcal*(icookwt/menucookwt),i_mealsum_kcal),
#          i_mealsum_protein=if_else(is.na(i_mealsum_protein),sum_protein*(icookwt/menucookwt),i_mealsum_protein),
#          i_mealsum_fat=if_else(is.na(i_mealsum_fat),sum_fat*(icookwt/menucookwt),i_mealsum_fat),
#          i_mealsum_carb=if_else(is.na(i_mealsum_carb),sum_carb*(icookwt/menucookwt),i_mealsum_carb),
#       i_mealsum_calcium=if_else(is.na(i_mealsum_calcium),sum_calcium*(icookwt/menucookwt),i_mealsum_calcium),
#     i_mealsum_iron=if_else(is.na(i_mealsum_iron),sum_iron*(icookwt/menucookwt),i_mealsum_iron))%>%
#   dplyr::select(-starts_with("sum_"))
# 
# nrow(filter(recipe_I,is.na(i_mealsum_kcal))) #180015 did not match

nutrition_2015_I = recipe_I%>%
  group_by(a01, mid) %>%
  filter(mealtaken==1)%>% #filter out if meal not taken
  dplyr::summarise(mealdata=n(),across(i_mealsum_kcal:i_mealsum_iron,sum,na.rm=TRUE))%>%
  rename_at(.vars=vars(contains("i_mealsum")),.funs=funs(sub("i_mealsum","I",.)))%>%
  filter(mid<100) #filter out guests

missing_I=nutrition_2015_I%>%
  filter(I_kcal<100|is.na(I_kcal)) #191 without calorie info, 1148 with less than 100 or no info


rm(recipe_I,recipe_hh)


```


****** Nutrition data comparison (TBD)
```{r food data check}
#There are multiple data sets to corroborate:
# HH reports food purchase/produced/gifted within the last 7 days on o1_female
# HH reports food group consumption over last 7 days on x3_female
# HH reports consumption over prior 24 hours on x1_female


#sevenday_items_o1 = aggregate(a01~o1_01, data=o1_female_2015, FUN = length) #295 items

#sevenday_groups_x3 = 

#oneday_items_x1 = 
  


```


5. Calculate BMI
```{r BMI calculation, include=FALSE,results='hide'}

adult_2015=w1_female_2015%>%
mutate(BMI=w1_03/((w1_04/100)^2))%>%
  mutate(BMI=na_if(BMI,0),pregnant=if_else(is.na(w1_01)|w1_01==2,0,1),lactating=if_else(is.na(w1_02)|w1_02==2,0,1))%>%
 dplyr::rename(weight=w1_03,height=w1_04)%>%
  dplyr::select(-starts_with("w1_"))

child_2015=w2_female_2015%>%
mutate(BMI=w2_07/((w2_08/100)^2))%>%
 dplyr::rename(weight=w2_07,height=w2_08)%>%
  dplyr::select(a01,mid,weight,height,hh_type,BMI)%>%
  mutate(pregnant=0,lactating=0)

anthro_2015_I=bind_rows(adult_2015,child_2015)

# dupe=anthro_2015_I%>%
#   group_by(a01,mid,hh_type)%>%
#   filter(n()>1)


rm(adult_2015,child_2015)
```

6. Create Individual Roster
```{r roster_I,results='hide'}


###CREATE INDIVIDUAL ROSTER###
#add BMI and nutrition consumption to individual roster_2015\



anthro_2015_I <- anthro_2015_I %>% select(!c("sex","age"))

roster_2015_I=left_join(b1_male_2015,anthro_2015_I,by=c("a01","mid")) %>%
  dplyr::rename(hhid=a01,sex=b1_01,age=b1_02,relation=b1_03,marital=b1_04,abroad=b1_05,literacy=b1_07,
                    education=b1_08,occupation=b1_10,sampletype=hh_type) %>%
  left_join(nutrition_2015_I,by=c("hhid"="a01","mid"))
         
 
nrow(filter(roster_2015_I,is.na(mealdata))) #8317 are missing mealdata
roster_2015_I$mealdata[is.na(roster_2015_I$mealdata)] <- 0
roster_2015_I$pregnant[is.na(roster_2015_I$pregnant)] <- 0
roster_2015_I$lactating[is.na(roster_2015_I$lactating)] <- 0
nrow(filter(roster_2015_I,is.na(BMI))) #8834 are missing BMI

occupation_type = aggregate(mid~occupation, data=roster_2015_I, FUN = length) %>%
  dplyr::rename(n_I=mid)%>%
  left_join(occupationcodes,by=c("occupation"="occupation_code")) %>%
  mutate(activity=if_else(occupation %in% c(1:8,10,15,22,30,54,64:71),"heavy",
                          if_else(occupation %in% c(11,23:27,29,31:37,54:63),"moderate",
                                  "light")))%>%
  dplyr::select(1,3,2,4)

#write.xlsx(occupation_type,"./Clean Data/occupations/occupation_category.xlsx")
#detach("package:plyr", unload = TRUE)

# add back activity level, count number of household members, and flag polygamous HH
roster_2015_I = roster_2015_I %>%
  left_join(occupation_type,by="occupation")%>%
  dplyr::select(-n_I,-occupation_name)%>%
  #filter(!relation %in% c(16)) %>%
  group_by(hhid)%>%
  dplyr::mutate(hhsize=n(),
         boy=if_else(age<18 & sex==1,1,0),
         girl=if_else(age<18 & sex==2,1,0),
         man=if_else(age>=18 & sex==1,1,0),
         woman=if_else(age>=18 & sex==2,1,0),
         adult=if_else(boy==0 & girl==0,1,0),
         child=if_else(man==0 & woman==0,1,0),
         otheradult=ifelse(relation>2 & adult==1,1,0),
         porl=if_else(pregnant==1 | lactating==1,1,0),
         spouseabroad=if_else(abroad==1 & relation==2,1,0))%>%
  ungroup()%>%
  group_by(hhid,relation)%>%
  dplyr::mutate(poly=if_else(n()>1 & relation==2,1,0)) %>%
  ungroup()%>%
  dplyr::select(-contains("b1"))

nrow(filter(roster_2015_I,poly==1)) #30 individuals are duplicate partners (ie: 15 hh have two spouses)
          
rm(occupation_type,occupationcodes,anthro_2015_I,nutrition_2015_I)
```



7. Create Household, Household Head, and Spouse Rosters
```{r roster_HH, echo=FALSE}

###create household level roster_2015 and add AE by OECD definition
roster_2015_hh = roster_2015_I %>%
  group_by(hhid) %>%
  dplyr::summarise(hhsize = n(), adult=sum(adult),child=sum(child), poly=max(poly),
            boy=sum(boy),girl=sum(girl),otheradult=sum(otheradult),
            porl_hh=sum(porl,na.rm=TRUE), spouseabroad_hh=sum(spouseabroad,na.rm=TRUE),
            mealdata_hhmin=min(mealdata),hh_kcal=sum(I_kcal,na.rm=TRUE),hh_protein=sum(I_protein,na.rm=TRUE),hh_fat=sum(I_fat,na.rm=TRUE),
            hh_carb=sum(I_carb,na.rm=TRUE),hh_calcium=sum(I_calcium,na.rm=TRUE),hh_iron=sum(I_iron,na.rm=TRUE),
            sampletype=first(sampletype)) %>%
  mutate(porl_hh=if_else(is.na(porl_hh),0,porl_hh),AE_OECD=1+0.5*(adult-1)+0.3*child)

#6503 households

#filter individual roster_2015 to create head and spouse roster_2015s
roster_2015_head = filter(roster_2015_I,relation==1) %>%
   mutate(agehead=age, sexhead=sex, 
          maritalhead=marital,
          abroadhead=if_else(abroad==1,1,0),
          lithead=if_else(literacy==4,1,0),
          noschoolhead=if_else(education==99,1,0),
          secondschoolhead=if_else(education %in% c(10:12,22,33),1,0),
          agworkhead=if_else(occupation %in% c(1,64:71),1,0),
          BMIhead=BMI,I_kcalhead=I_kcal) %>%
  dplyr::select(hhid,contains("head"))
#6503 heads          
          
roster_2015_spouse = filter(roster_2015_I,relation==2) %>%
            mutate(agespouse=age,sexspouse=sex,
                   abroadspouse=if_else(abroad==1,1,0),
                   litspouse=if_else(literacy==4,1,0),
                   noschoolspouse=if_else(education==99,1,0),
                   secondschoolspouse=if_else(education %in% c(10:12,22,33),1,0),
                   agworkspouse=if_else(occupation %in% c(1,64:71),1,0),
                   BMIspouse=BMI,I_kcalspouse=I_kcal)%>%
  dplyr::select(hhid,ends_with("spouse"))
#5225 spouses

#add head and spouse characteristics back to household level roster_2015                   
roster_2015_hh=full_join(roster_2015_hh,roster_2015_head,by="hhid") 
roster_2015_hh=full_join(roster_2015_hh,roster_2015_spouse,by="hhid")
#6518 households = 6503+15 additional spouses in poly hh



dupe_hh = roster_2015_hh %>%
  #filter(sampletype==2 |sampletype==3)%>% 
  group_by(hhid) %>% 
  filter(n() > 1)#30 poly HH 

roster_2015_hh= distinct(roster_2015_hh,hhid, .keep_all= TRUE) #keeps only one line for each poly HH because HH level var are equivalent

rm(roster_2015_head,roster_2015_spouse,dupe_hh)

```

8. Calculate village level prices and HH expenditures
```{r expenditures, echo=FALSE,include=FALSE,results='hide'}

#task: change vcode_n to Village
villages = aggregate(a01~Village, data=a_male_2015, FUN = length) #318 villages
upazilla = aggregate(a01~uzcode, data=a_male_2015, FUN = length) #279 upazilla


#calculate household level weekly food expenditure
foodexp_2015 = left_join(o1_female_2015,a_male_2015,by="a01")%>%
  dplyr::select(a01,contains("o1"),Village,dcode)%>%
  mutate(o1_07a=if_else(o1_04 %in% c(1,2,3),o1_08/o1_06,o1_08/o1_05)) #category 1 is kg, cat 2 is g, 3 is liter, and now 4 is g
  #mutate(o1_06a=if_else(o1_04==2,o1_06/1000,o1_06), #change grams into kilos 
        # o1_07a=if_else(o1_04==4,(o1_08/o1_05)/1000,o1_07))%>% #alternate unit price=total val/number of kg reported

  
missing_exp=foodexp_2015%>%
  filter(is.na(o1_07a))

#calculate village level prices: unit mean and unit median prices if there are more than 3 observations in the village for the food item
# prices_village = o1_f_2015_hh%>%
#   dplyr::select(vcode_n,dcode,o1_01,o1_04,o1_06,o1_07,o1_08)%>%
#   arrange(dcode,vcode_n,o1_01,o1_04,o1_07)%>%
#   group_by(o1_01,vcode_n) %>%
#   filter(!is.na(o1_07))%>%
#   dplyr::summarise(unitprice=ifelse(n()>3,mean(o1_07),0),medprice=ifelse(n()>3,median(o1_08/o1_06),0))%>%
#   dplyr::na_if(0) #convert zero to NA

prices=foodexp_2015%>%
  dplyr::select(o1_01,o1_04,o1_06,o1_07,o1_07a,o1_08)%>%
  #arrange(o1_01,o1_04)%>%
  group_by(o1_01,o1_04) %>%
dplyr::summarise(mp=median(o1_07a,na.rm=TRUE))

  # filter(!is.na(o1_07))%>%
  # dplyr::summarise(unitprice=ifelse(n()>3,mean(o1_07),0),medprice=ifelse(n()>3,median(o1_08/o1_06),0))%>%
  # dplyr::na_if(0) #convert zero to NA

#join food expenditures with village food prices
foodexp_2015 = left_join(foodexp_2015,prices,by=c("o1_01","o1_04"))%>%
  mutate(foodprod=mp*o1_10,foodother=mp*o1_11) %>%
 dplyr::na_if(0) #convert zero to NA
  
foodexp_2015_hh = foodexp_2015%>%
  group_by(a01) %>%
  dplyr::summarise(foodpurch_hhwk=sum(o1_08,na.rm=TRUE),foodprod_hhwk=sum(foodprod,na.rm=TRUE),
            foodother_hhwk=sum(foodother,na.rm=TRUE))%>%
  mutate(foodtot_hhwk=rowSums(.[2:3],na.rm=TRUE)) #only include purch and prod


#calculate household level weekly nonfood expenditure from monthly
nonfoodexp_2015_m = p1_male_2015 %>%
  group_by(a01) %>%
  dplyr::summarise(p1_02=sum(p1_02,na.rm=TRUE),p1_04=sum(p1_04,na.rm=TRUE)) %>%
  mutate(nonfoodexp1_hhwk=(p1_02+p1_04)*12/52) 

#calculate household level weekly nonfood expenditure from annual
nonfoodexp_2015_y = p2_male_2015 %>%
  group_by(a01) %>%
  dplyr::summarise(p2_03=sum(p2_03,na.rm=TRUE),p2_06=sum(p2_06,na.rm=TRUE)) %>%
  mutate(nonfoodexp2_hhwk=(p2_03+p2_06)/52)    

#combine all nonfood exp expenditures
nonfoodexp_2015_hh=left_join(nonfoodexp_2015_m,nonfoodexp_2015_y,by="a01") %>%
  mutate(nonfoodexp_hhwk=nonfoodexp1_hhwk + nonfoodexp2_hhwk) %>%
  dplyr::select(a01,nonfoodexp_hhwk)



#add food expenditures to household roster_2015
roster_2015_hh=left_join(roster_2015_hh,nonfoodexp_2015_hh,by=c("hhid"="a01")) %>%
  mutate(nonfoodexp_hhwk_pc=nonfoodexp_hhwk/hhsize,
         nonfoodexp_hhwk_AE_OECD=nonfoodexp_hhwk/AE_OECD)%>%
left_join(foodexp_2015_hh,by=c("hhid"="a01")) %>%
  mutate(foodpurch_hhwk_pc = foodpurch_hhwk/hhsize,
    foodpurch_hhwk_AE_OECD = foodpurch_hhwk/AE_OECD,
    foodtot_hhwk_pc = foodtot_hhwk/hhsize,
    foodtot_hhwk_AE_OECD = foodtot_hhwk/AE_OECD)%>%
  mutate(foodshare=if_else(nonfoodexp_hhwk>0 & foodtot_hhwk>0,foodtot_hhwk/(foodtot_hhwk+nonfoodexp_hhwk),0),
         totexp_hhwk=nonfoodexp_hhwk+foodtot_hhwk)

#dplyr::na_if(roster_2015_hh$foodshare,0) #convert zero to NA

rm(nonfoodexp_m_hh,nonfoodexp_y_hh,upazilla,villages,prices,foodexp_2015,foodexp_2015_hh,nonfoodexp_2015_hh,nonfoodexp_2015_m,nonfoodexp_2015_y,missing_exp)

```

9. Food Security measures (hdds tbd)
```{r food security, echo=FALSE}

foodsecurity=x3_female_2015%>%
  dplyr::rename(hhid=a01,nofood_freq=x3_02,hungrynight_freq=x3_04,hungryday_freq=x3_06)%>%
  mutate(nofood=if_else(x3_01==1,1,0),hungrynight=if_else(x3_03==1,1,0),hungryday=if_else(x3_05==1,1,0))%>%
  mutate(cereal_days=x3_07_1+x3_07_2+x3_07_4,
         tuber_days=x3_07_3,
         vegetable_days=x3_07_5,
         fruit_days=x3_07_6 ,
         meat_days=x3_07_10+x3_07_11,
         egg_days=x3_07_8,
         seafood_days=x3_07_12 ,
         pulse_days=x3_07_7+x3_07_16,
         milk_days=x3_07_9,
         fat_days=x3_07_13 ,
         sugar_days=x3_07_14 ,
         misc_days=x3_07_15+x3_07_17)%>%
  mutate_at(.vars=vars(contains("days")),.funs=list(~as.numeric(.)))%>%
    mutate_at(.vars=vars(contains("days")),.funs=list(~if_else(.>7,7,.)))%>%
mutate_at(.vars=vars(contains("days")),.funs=funs(`1`=if_else(.>0,1,0)))%>%
rename_at(.vars=vars(contains("days")),.funs=funs(sub("_days_1","",.)))%>%
   dplyr::select(-contains("x"))%>%
mutate(hhds=rowSums(.[21:32],na.rm=TRUE))%>%
  dplyr::select(hhid,hhds,contains("food"),contains("hungry"),-contains("freq"),-contains("seafood"))


# fx=function(x){
#   mutate(temp=if_else(x>0,1,0))
#   dplyr::rename(gsub("_days","",x)==temp)
# }
          
          

  
#add back to HH level roster
roster_2015_hh=left_join(roster_2015_hh,foodsecurity,by="hhid")


rm(foodsecurity)

```



10. (tbd) Assistance Type
```{r assistance, echo=FALSE}
#breakdown of assistance type (for all households)
# assistance = u_male_2015 %>%
#   filter(u01==1) 
# 
# assistance_count = aggregate(a01~slno, data=assistance, FUN = length)

# %>%
#   group_by(a01)%>%
#   summarise(u01_hh=n(mid_1)+n(mid_2))
```


Select variables from BIHS data

1.1 select C data (Non-ag employment)
```{r}
#select household id and income variables(c14)
nonag_employment = c_male_2015%>%
  dplyr::select("a01","c14")%>%
  dplyr::rename(hhid = a01, nonag_income = c14)%>%
  group_by(hhid)%>%
  dplyr::summarise(across(everything(), sum, na.rm = TRUE))

```

1.2 select D1 & D2 data (assets)
```{r}
#select variables of purchase price(D1_09,D2_09)and current values(D1_10,D2_10)
assets = d1_male_2015%>%
  left_join(d2_male_2015, by=c("a01"))%>%
  dplyr::select("a01","d1_09","d1_10","d2_09","d2_10")%>%
  dplyr::rename(hhid = a01, purchase_val=d1_09,curr_val=d1_10,ag_purchase_val=d2_09,ag_curr_val=d2_10)%>%
  dplyr::summarise(across(everything(), sum, na.rm = TRUE))
  
# task:use summarise instead
  # group_by("hhid")%>%
  # dplyr::summarise(purchase_val=sum(purchase_val,na.rm=TRUE)

```

1.3 select E data (savings)
```{r}
savings = e_male_2015%>%
  dplyr::select("a01","e01","e02","e06")%>%
  dplyr::rename(hhid=a01,anysaving_pastyr = e01,anysaving_curr = e02, total_saving = e06)%>%
  group_by(hhid)%>%
  dplyr::summarise(anysaving_pastyr=mean(anysaving_pastyr,na.rm=TRUE),anysaving_curr=mean(anysaving_curr,na.rm=TRUE),total_saving = sum(total_saving, na.rm = TRUE))

#change yes/no(1/2) to 1/0
savings[savings$anysaving_pastyr== 2, ]$anysaving_pastyr = 0
savings[savings$anysaving_curr== 2, ]$anysaving_curr = 0
  
```

1.4 select F data (loans)
```{r}
loans = f_male_2015%>%
  dplyr::select("a01","f01","f02","f07")%>%
  dplyr::rename(hhid=a01,anyloan = f01,anyloan_curr = f02, total_loan = f07)%>%
  group_by(hhid)%>%
  dplyr::summarise(anyloan=mean(anyloan,na.rm=TRUE),anyloan_curr=mean(anyloan_curr,na.rm=TRUE),total_loan = sum(total_loan, na.rm = TRUE))

#change yes/no(1/2) to 1/0
loans[loans$anyloan== 2, ]$anyloan = 0
loans[loans$anyloan_curr== 2, ]$anyloan_curr = 0
```

1.5 select G data (land)
```{r}
land = g_male_2015%>%
  dplyr::select("a01","g10")%>%
  dplyr::rename(hhid=a01,market_val = g10)%>%
  group_by(hhid)%>%
  dplyr::summarise(market_val=sum(market_val,na.rm=TRUE))
  
```

1.6 select H data (Ag production)
```{r}
ag_plot = h1_male_2015%>%
  dplyr::select("a01","h1_03")%>%
  dplyr::rename(hhid=a01,area_planted = h1_03)%>%
  group_by(hhid)%>%
  dplyr::summarise(area_planted=sum(area_planted,na.rm=TRUE))
```

1.7 select I1 data (Summary of Agriculture Production)

```{r}
# select i1 data, drop "sample type" column that is not necessary
# code NA to zero
Ag_production = i1_male_2015%>%
  dplyr::rename(hhid=a01)%>%
  group_by(hhid)%>%
  dplyr::summarise(agsales=sum(i1_13,na.rm=TRUE))%>%
  dplyr::select(hhid,agsales)
```

1.8 select I2 data (Food Grain Stock and Storage Capacity)

```{r}
#Goal: hh level variables for the maximum number of months of any grain stock  
  #first pivot longer so we each observation is a hhid-grain pair
  #group by hh and summarise by creating a binary variable for each money if the hh had any grain stocks
  #count the number of months for which that binary variable is greater than zero for each hh

grain_stock = i2_male_2015%>%
    dplyr::rename(hhid = a01)%>%
  pivot_longer(cols = i2_02_1:i2_13_3,names_to = c("grain_month", "crop"),
  names_pattern = "i2_?(.*)_(.*)", values_to="qty") %>%
  #question: code 99999 (without stock) to zero
  mutate(qty = if_else(qty<99999,qty,0))
  

grain_stock$grain_month = ifelse(str_detect(grain_stock$grain_month, fixed("02")),"Dec",
                         ifelse(str_detect(grain_stock$grain_month, fixed("03")),"Jan",
                         ifelse(str_detect(grain_stock$grain_month, fixed("04")),"Feb",
                         ifelse(str_detect(grain_stock$grain_month, fixed("05")),"Mar",
                         ifelse(str_detect(grain_stock$grain_month, fixed("06")),"Apr",
                         ifelse(str_detect(grain_stock$grain_month, fixed("07")),"May",
                         ifelse(str_detect(grain_stock$grain_month, fixed("08")),"Jun",
                         ifelse(str_detect(grain_stock$grain_month, fixed("09")),"Jul",
                         ifelse(str_detect(grain_stock$grain_month, fixed("10")),"Aug",
                         ifelse(str_detect(grain_stock$grain_month, fixed("11")),"Sep",
                         ifelse(str_detect(grain_stock$grain_month, fixed("12")),"Oct",
                         "Nov")))))))))))

grain_stock=grain_stock%>%
  group_by(hhid,grain_month)%>%
  dplyr::summarise(store_capacity_kg=mean(i2_14,na.rm=TRUE),tot_qty=sum(qty,na.rm=TRUE))%>%
  ungroup()%>%
 mutate(any_grain=if_else(tot_qty>0,1,0))%>%
  group_by(hhid)%>%
  dplyr::summarise(store_capacity_kg=mean(store_capacity_kg),nmo_anygrain=sum(any_grain))%>%
ungroup()

```

1.9 select N data (Non-ag income)
```{r}
nonag_income = n_male_2015%>%
  dplyr::select("a01","n05")%>%
  dplyr::rename(hhid=a01,profit_12mon = n05)%>%
  group_by(hhid)%>%
  dplyr::summarise(profit_12mon=sum(profit_12mon,na.rm=TRUE))
```

1.10 select R01/R06a data (Sanitation and Water; R01 = latrine type, R03 = water source)

```{r}
#select r01 and r06a columns and rename variables
#create binary variable =1 if HH had any HH-based latrine (r01=2,3,4,5)
# create binary varibale = 1 if drinking is filtered or treated (r06=1,2,3,4,6)
latrine_water = r_male_2015%>%
  dplyr::select("a01", "r01", "r06a")%>%
  dplyr::rename(hhid = a01, latrine_type = r01, drinkwater_source = r06a)%>%
  mutate(hh_lat = ifelse(latrine_type %in% c(2,3,4,5), 1,0),treated_drinkwater = ifelse(drinkwater_source %in% c(1,2,3,4,6), 1,0))%>%
  dplyr::select(hhid,hh_lat,treated_drinkwater)



```

1.11 select T1 data (Negative Shocks)
```{r}
# filter all the household having any negative shocks
neg_shock = t1_male_2015%>%
  dplyr::rename(hhid = a01)%>%
  group_by(hhid)%>%
  dplyr::summarise(negshock_no=n(),negshock_val=sum(t1_07,na.rm=TRUE))

```

1.12 select T2 data (Positive Events)
```{r}
pos_shock = t2_male_2015%>%
  filter(t2_03==1)%>%
  dplyr::rename(hhid = a01)%>%
   group_by(hhid)%>%
  dplyr::summarise(posshock_no=n(),posshock_val=sum(t2_06,na.rm=TRUE))

```

1.13 select U data (Social Safety Net Programs)

```{r}
# select u data and rename variables
#question: what to do with u09 and u10? u09 is the Other in-kind sobsidy code, u10 is number
social_safety = u_male_2015%>%
  filter(u01==1&hh_type%in%c(2,3))%>%
  dplyr::rename(hhid = a01)%>%
  group_by(hhid)%>%
  dplyr::rename(cash_received = u02)%>%
  mutate(rice_val=if_else(is.finite(u03),u03*u04,as.numeric(NA)),wheat_val=if_else(is.finite(u05),u05*u06,as.numeric(NA)))%>%
  dplyr::select(hhid,slno,hh_type,cash_received,rice_val,wheat_val,u07,u08)%>%
plyr::mutate(inkind_val=rowSums(.[5:8],na.rm=TRUE))%>% 
  group_by(hhid)%>%
  dplyr::summarise(prog_ct=n(),cash_received=sum(cash_received,na.rm=TRUE),inkind_val=sum(inkind_val,na.rm=TRUE))

```

1.14 select v4 data (Other Income Household)
```{r}
other_income = v4_male_2015%>%
  mutate(tot_othinc=rowSums(.[3:14],na.rm=TRUE))%>%
  dplyr::rename(hhid = a01)%>%
  dplyr::select(hhid,tot_othinc)

```
   

1.15 select y6a data (access to clinics)

```{r}
# selected columns 
clinic_access = y6a_female_2015%>%
  dplyr::select("a01", "hh_type","y6a_01","y6a_02","y6a_03")%>%
  dplyr::rename(hhid=a01, know_clinic = y6a_01, commute_min = y6a_02, any_usage = y6a_03)
  # pivot_longer(cols = y6a_04_1:y6a_04_3, names_to = "y6a_04",values_drop_na = TRUE)%>%
  # dplyr::select(-y6a_04)%>%
  # dplyr::rename(y6a_04=value)

# create a new dummy variable `clinic_access` to show whether household have access to clinic
clinic_access$clinic_access = ifelse((clinic_access$commute_min == 999), 0, 1)
```

1.16 select y8 data (health worker visits)

```{r}
# select health worker and group meeting data
# Question: Do we want to code visits from last THREE month? (y8_01a- y8_04a)
CHW_visit = y8_female_2015%>%
  dplyr::select("a01","y8_01","y8_02","y8_03","y8_04",contains("y8_05"),"y8_06",contains("y8_07"))%>%
  dplyr::rename(hhid = a01, visit_sixmo = y8_01, health_org = y8_02, num_visited_sixmo = y8_03, any_advice = y8_04, advice1 = y8_05_1,advice2 = y8_05_2,advice3 = y8_05_3,advice4 = y8_05_4, any_grpdiscuss = y8_06, discuss_topics1 = y8_07_1,discuss_topics2 = y8_07_2,discuss_topics3 = y8_07_3,discuss_topics4 = y8_07_4)

#recode all yes/no variables, so that "no" is equal to zero, as it is coded as 2 in the codebook
#Question: is it okay for 88 it is coded to zero as well (88 = don't know)(did in 2011)
CHW_visit[is.na(CHW_visit$visit_sixmo), ]$visit_sixmo = 0
CHW_visit[CHW_visit$visit_sixmo == 2, ]$visit_sixmo = 0
CHW_visit[CHW_visit$visit_sixmo == 88, ]$visit_sixmo = 0

CHW_visit[is.na(CHW_visit$num_visited_sixmo), ]$num_visited_sixmo = 0
CHW_visit[CHW_visit$num_visited_sixmo == 88, ]$num_visited_sixmo = 0

#replace the NA values first with 0
CHW_visit[is.na(CHW_visit$any_advice), ]$any_advice = 0
CHW_visit[CHW_visit$any_advice == 2, ]$any_advice = 0

#count the number of household that has visits and has advice - there are a large difference
nrow(CHW_visit[CHW_visit$visit_sixmo == 1,])
nrow(CHW_visit[CHW_visit$any_advice == 1,])
```

1.17 merge all modules to the roster
```{r}
w.hh.roster.2015=roster_2015_hh%>%
  left_join(nonag_employment,by=c("hhid"))%>%
  left_join(assets,by=c("hhid"))%>%
  left_join(savings,by=c("hhid"))%>%
  left_join(loans,by=c("hhid"))%>%
  left_join(land,by=c("hhid"))%>%
  left_join(ag_plot,by=c("hhid"))%>%
  left_join(Ag_production,by=c("hhid"))%>%
  left_join(grain_stock,by=c("hhid"))%>%
  left_join(nonag_income,by=c("hhid"))%>%
  left_join(latrine_water,by=c("hhid"))%>%
  left_join(neg_shock,by=c("hhid"))%>%
  left_join(pos_shock,by=c("hhid"))%>%
  left_join(social_safety,by=c("hhid"))%>%
  left_join(other_income,by=c("hhid"))%>%
  left_join(clinic_access,by=c("hhid"))%>%
  left_join(CHW_visit,by=c("hhid"))

```



Descriptives
D1. Summary of unweighted sample (6503 HH)
```{r total sample, echo=FALSE}

### SUMMARY of all 6503 households (ie: 15 hh dropped with two spouses)
summary.hh.2015= roster_2015_hh %>%
    psych::describe() %>%
  as_tibble(rownames="rowname") %>%
  dplyr::select(rowname,n,mean,sd)

#print(roster_2015_hh.summary,digits=3)


```


D2. Add survey weights and restrict to representative sample (5503 HH)
```{r summary, echo=FALSE}



hh_type = aggregate(hhid~sampletype, data=roster_2015_hh, FUN = length)
#1:FTF Original 1000
#2:FTF Additional 1080
#3:National Representative 4423

#import weights
weights_2015 <- read_dta("./Data/Raw Data/bihs_2015/IFPRI_BIHS_R2_exp.dta") %>%
  dplyr::select(a01,dvcode,vcode,aeu,hhweightR2,popweightR2)

#choose sample type 2 and 3, eliminate poly households
w.hh.roster.2015=left_join(roster_2015_hh,weights_2015,by=c("hhid"="a01"))%>%
  filter(sampletype==2 |sampletype==3)
#%>%filter(poly==0&spouseabroad_hh==0)

#choose sample type 2 and 3, eliminate poly households & children under 1 & individuals w/out mealdata
w.I.roster.2015=left_join(roster_2015_I,weights_2015,by=c("hhid"="a01"))%>%
  filter(sampletype==2 |sampletype==3)%>%
  filter(I_kcal>0 & mealdata>0 &age>=2)%>%
   dplyr::select(-poly,-mealdata)
#&poly==0&abroad==2&spouseabroad==0)

 


design_HH <- svydesign(data=w.hh.roster.2015,id=~vcode, strata=~dvcode,weights=~hhweightR2)
design_I <- svydesign(data=w.I.roster.2015,id=~vcode, strata=~dvcode,weights=~popweightR2)


# summary.w.hh.2015= w.hh.roster.2015 %>%
#   dplyr::select(hhsize,adult,child,totexp_hhwk,foodshare,hhds,contains("head"),contains("spouse"),vcode,dvcode,popweight1)%>%
#     psych::describe() %>%
#   as_tibble(rownames="rowname") %>%
#   dplyr::select(rowname,n,mean,sd)


listx = dplyr::select(w.hh.roster.2015,hhsize,adult,child,totexp_hhwk,foodshare,hhds,contains("head"),contains("spouse"),-contains("abroad"))%>%
  mutate_at(.vars=vars(contains("sex")),.funs=list(~recode(.,"2=0")))%>%
  mutate(maritalhead=if_else(maritalhead==2,1,0))
  #-contains("sex"),-contains("marital"))

a=svymean(listx,design_HH,na.rm=TRUE)
#ab=print(ftable(a),rownames=c("Household Size","Number of Adults","Number of Children"),digits=2)
ab=as.data.table(a,keep.rownames=T)

ab$rownames<-c("Size","Number of Adults","Number of Children","Total Weekly Expenditure (2012 Taka)","Food Share of Total Expenditure","Household Dietary Diversity Score","Age (Years)","Male ","Married ","Literacy ","No Schooling ","Secondary Schooling ","Agricultural Worker ","Body Mass Index (BMI)","Reported Calorie Consumption (kcal)","Age (Years)","Male ","Literacy ","No Schooling ","Secondary Schooling ","Agricultural Worker ","Body Mass Index (BMI)","Reported Calorie Consumption (kcal)")

abc=ab%>%
  dplyr::select(rownames,mean,SE)%>%
   mutate(mean=if_else(mean<1,paste0(round(mean*100,2),"%"),as.character(round(mean,2))))
  


descriptives=kable(abc,booktabs=TRUE,digits=3,
                   col.names=c("Variable","Weighted Mean","SD"),escape=F)%>%
  kable_styling(full_width=FALSE,bootstrap_options = "condensed")%>%
  pack_rows("Household",1,6)%>%
pack_rows("Household Head",7,15)%>%
 pack_rows("Spouse of Household Head",16,23)%>% 
 footnote(general="Data are population-weighted means and standard deviations using sample weights provided by IFPRI")


print(descriptives)

save_kable(descriptives,"./Output/2015/outputBIHS_Projectdescriptives.png")


#a=qflextable(ab)
#write.table(ab,file="D:/UIUC/SP21/BIHSgit/BIHS_Project/Programs/R/output/descriptives.doc")


rm(listx,ab,a,abc)

```




Clean up global environment
```{r}

rm(list=ls(pattern="male")) 
   
```






Import reference standards

I.1 Import India Reference standards and Energy Requirements
```{r India}



#INDIA requirements and AE
#read in adult equivalent from India
AE_India <-read_excel("./Data/Clean Data/nutrient standards/GuidelinesIndia_2011.xlsx",sheet="AE_India",range = "A1:D13",col_types =  "numeric")


#join AE 
#task: use column names instead of index to deselect columns
w.I.roster.2015=fuzzy_left_join(w.I.roster.2015,AE_India, 
                by=c("age"="agemin", "age"="agemax"),
                match_fun=list(`>=`, `<=`))%>%
  mutate(AE_India_grp=if_else(sex==1,AE_male,if_else(sex==2 & porl==1,1.17,AE_female)))%>%
  dplyr::select(-c("agemin","agemax","AE_male","AE_female"))
#,"agemin.x","agemin.y","agemax.x","agemax.y","AE_male.x","AE_female.x","AE_male.y","AE_female.y"))

#India Dietary requirements
India_RDA<-read_excel("./Data/Clean Data/nutrient standards/GuidelinesIndia_2011.xlsx",sheet="India_RDA",range = "A1:k19",col_names = TRUE)%>%
  mutate(sex=if_else(sex=="male",1,2),agemin=as.numeric(agemin),agemax=as.numeric(agemax),
         activity=if_else(is.na(activity),"moderate",activity))%>%
  dplyr::select(-1)


#join India requirements (all are using ref weight and height, and assume moderate activity for under 18 p66 Inida (2009))
#task: unselect agemin and agemax in w.I roster.2015
w.I.roster.2015=w.I.roster.2015%>%
  #select(!c("agemin","agemax"))%>%
  mutate(activityI=if_else(age>=18,activity,"moderate"))%>%
  fuzzy_left_join(India_RDA,
                by=c("sex","activityI"="activity","age"="agemin", "age"="agemax"),
                match_fun=list(`==`,`==`,`>=`, `<=`))%>%
   dplyr::rename(activity=activity.x,sex=sex.x,weight_India_grp=refwt_India)%>%
  mutate(age_grp_India=if_else(!is.na(agemin),paste(as.character(agemin),as.character(agemax),sep="-"),as.character(NA)),
    kcal_India_grp=if_else(pregnant==1,kcal_India+350,if_else(lactating==1,kcal_India+560,kcal_India))
       ,protein_rda_India=if_else(pregnant==1,protein_rda_India+23,if_else(lactating==1,protein_rda_India+16,protein_rda_India)),
    #calcium_rda_India=if_else(porl==1,1200,calcium_rda_India),
    #iron_rda_India=if_else(porl==1,21,iron_rda_India)
    )%>%
  dplyr::select(-contains(".y"),-agemin,-agemax,-calcium_rda_India,-iron_rda_India,-kcal_India)

#task : the columns of w.I roster.2015 are different from those of  w.I roster.2011
rm(list=ls(pattern="India"))


```


I.2 Import FAO height weight and BMI reference standards and energy Requirements
```{r FAO}



#FAO weight height
hfa_girls_24 <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="hfa_girls_25",col_names = TRUE)%>%
  mutate(year=floor(Month/12),month=Month-year*12,sex=2)%>%
    dplyr::rename_at(.vars=vars(contains("P")),.funs=funs(paste("h",.,sep="_")))%>%
  dplyr::select(sex,year,month,contains("h_P"))%>%
  filter(year%in%(2:4))%>%
  mutate(h_med=h_P50)

wfa_girls_24 <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="wfa_girls_05",col_names = TRUE)%>%
  mutate(year=floor(Month/12),month=Month-year*12,sex=2)%>%
    dplyr::rename_at(.vars=vars(contains("P")),.funs=funs(paste("w",.,sep="_")))%>%
  dplyr::select(sex,year,month,contains("w_P"))%>%
  filter(year%in%(2:4))%>%
  mutate(w_med=w_P50)

girls_24=left_join(hfa_girls_24,wfa_girls_24,by=c("sex","year","month"))

hfa_girls_519 <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="hfa_girls_519",col_names = TRUE)%>%
   mutate(year=floor(Month/12),month=Month-year*12,sex=2)%>%
    dplyr::rename_at(.vars=vars(contains("P")),.funs=funs(paste("h",.,sep="_")))%>%
  dplyr::select(sex,year,month,contains("h_P"))%>%
  mutate(h_med=h_P50)

wfa_girls_510 <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="wfa_girls_510",col_names = TRUE)%>%
mutate(year=floor(Month/12),month=Month-year*12,sex=2)%>%
    dplyr::rename_at(.vars=vars(contains("P")),.funs=funs(paste("w",.,sep="_")))%>%
  dplyr::select(sex,year,month,contains("w_P"))%>%
  mutate(w_med=w_P50)

bmi_girls_519 <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="bmi_girls_519",col_names = TRUE)%>%
mutate(year=floor(Month/12),month=Month-year*12,sex=2)%>%
    dplyr::rename_at(.vars=vars(contains("P")),.funs=funs(paste("b",.,sep="_")))%>%
  dplyr::select(sex,year,month,contains("b_P"))%>%
  mutate(b_med=b_P50)

girls_519=left_join(hfa_girls_519,wfa_girls_510,by=c("sex","year","month"))%>%
  left_join(bmi_girls_519,by=c("sex","year","month"))%>%
  mutate(w_med=if_else(is.na(w_med),b_med*(h_med/100)^2,w_med))

girls=bind_rows(girls_24,girls_519)

girls_19=girls%>%
  filter(year==19)%>%
  dplyr::select(contains("med"))

women_20=tibble(year=seq(20,120,1),sex=2,h_med=girls_19$h_med,w_med=girls_19$w_med)

FAO_women=bind_rows(girls,women_20)%>%
  mutate(w_med=if_else(is.na(w_med)&year<19,b_med*(h_med/100)^2,w_med))%>%
  group_by(sex,year)%>%
   dplyr::summarise(across(everything(),median,na.rm=TRUE))%>%
  dplyr::select(-month)%>%
  mutate(pregnant=0,lactating=0)

FAO_women_med=FAO_women%>%
  dplyr::select(sex,year,contains("_med"),pregnant,lactating)


for(i in 14:50){
  x=FAO_women_med%>%
    filter(year==i)%>%
    mutate(pregnant=1,b_med=as.numeric(NA),w_med=w_med+13.25)
  
  y=FAO_women_med%>%
    filter(year==i)%>%
    mutate(lactating=1)
  
  FAO_women_med=rbind(FAO_women_med,x,y)
}
    
rm(list=ls(pattern="girls"),women_20,x,y)
 

hfa_boys_24 <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="hfa_boys_25",col_names = TRUE)%>%
  mutate(year=floor(Month/12),month=Month-year*12,sex=1)%>%
    dplyr::rename_at(.vars=vars(contains("P")),.funs=funs(paste("h",.,sep="_")))%>%
  dplyr::select(sex,year,month,contains("h_P"))%>%
  filter(year%in%(2:4))%>%
  mutate(h_med=h_P50)

wfa_boys_24 <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="wfa_boys_05",col_names = TRUE)%>%
  mutate(year=floor(Month/12),month=Month-year*12,sex=1)%>%
    dplyr::rename_at(.vars=vars(contains("P")),.funs=funs(paste("w",.,sep="_")))%>%
  dplyr::select(sex,year,month,contains("w_P"))%>%
  filter(year%in%(2:4))%>%
  mutate(w_med=w_P50)

boys_24=left_join(hfa_boys_24,wfa_boys_24,by=c("sex","year","month"))


hfa_boys_519 <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="hfa_boys_519",col_names = TRUE)%>%
   mutate(year=floor(Month/12),month=Month-year*12,sex=1)%>%
    dplyr::rename_at(.vars=vars(contains("P")),.funs=funs(paste("h",.,sep="_")))%>%
  dplyr::select(sex,year,month,contains("h_P"))%>%
  mutate(h_med=h_P50)

wfa_boys_510 <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="wfa_boys_510",col_names = TRUE)%>%
mutate(year=floor(Month/12),month=Month-year*12,sex=1)%>%
    dplyr::rename_at(.vars=vars(contains("P")),.funs=funs(paste("w",.,sep="_")))%>%
  dplyr::select(sex,year,month,contains("w_P"))%>%
  mutate(w_med=w_P50)

bmi_boys_519 <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="bmi_boys_519",col_names = TRUE)%>%
mutate(year=floor(Month/12),month=Month-year*12,sex=1)%>%
    dplyr::rename_at(.vars=vars(contains("P")),.funs=funs(paste("b",.,sep="_")))%>%
  dplyr::select(sex,year,month,contains("b_P"))%>%
  mutate(b_med=b_P50)

boys_519=left_join(hfa_boys_519,wfa_boys_510,by=c("sex","year","month"))%>%
  left_join(bmi_boys_519,by=c("sex","year","month"))%>%
  mutate(w_med=if_else(is.na(w_med),b_med*(h_med/100)^2,w_med))

boys=bind_rows(boys_24,boys_519)

boys_19=boys%>%
  filter(year==19)%>%
  dplyr::select(contains("med"))

men_20=tibble(year=seq(20,120,1),sex=1,h_med=boys_19$h_med,w_med=boys_19$w_med) 

FAO_men=bind_rows(boys,men_20)%>%
  mutate(w_med=if_else(is.na(w_med)&year<19,b_med*(h_med/100)^2,w_med))%>%
  group_by(sex,year)%>%
   dplyr::summarise(across(everything(),median,na.rm=TRUE))%>%
  dplyr::select(-month)%>%
  mutate(pregnant=0,lactating=0)

FAO_men_med=FAO_men%>%
  dplyr::select(sex,year,contains("_med"),pregnant,lactating)

rm(list=ls(pattern="boys"),men_20)

FAO_hwb=bind_rows(FAO_women,FAO_men)

FAO_hwb_med=bind_rows(FAO_women_med,FAO_men_med)%>%
  mutate(age_grp_FAO=if_else(year%in%(4:8),"4-8",if_else(year%in%(9:13),"9-13",if_else(year%in%(14:18),"14-18",if_else(year%in%(19:30),"19-30",if_else(year%in%(31:50),"31-50",if_else(year%in%(51:69),"51-69",if_else(year>=70,"70 and over",as.character(year)))))))))%>%
  dplyr::rename(age=year)%>%
  group_by(sex,age_grp_FAO)%>%
  dplyr::mutate(h_FAO_grp=median(h_med),w_FAO_grp=median(w_med))%>%
  dplyr::rename(h_FAO=h_med,w_FAO=w_med,b_FAO=b_med)

rm(list=ls(pattern="men"))


#read in energy requirement formulas
FAO_adult <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="Adult_BMRPAL",range = "A1:M37",col_names = TRUE)%>%
  dplyr::select(1:6,9:11,13)%>%
  mutate(sex=if_else(sex=="Male",1,2))%>%
  filter(agemin>=18)

FAO_child <- read_excel("./Data/Clean Data/nutrient standards/WHOFAO_requirements_2011.xlsx",sheet="Child_TEEPAL",range = "A1:P97",col_names = TRUE)%>% 
  mutate(sex=if_else(sex=="Male",1,2))%>%
dplyr::select(1:6,11,13,14,16)

FAO=bind_rows(FAO_adult,FAO_child)


FAO_energy=FAO_hwb_med%>%
    fuzzy_left_join(FAO,by=c("sex"="sex","age"="agemin","age"="agemax"),match_fun=list(`==`,`>=`,`<`))%>%
  dplyr::rename(sex=sex.x)%>%
  dplyr::select(-sex.y,-agemin,-agemax)%>%
 mutate(protein_FAO_age=if_else(pregnant==1,protein_FAO_perkg*w_FAO+14,
                                if_else(lactating==1,protein_FAO_perkg*w_FAO+15.75,
                                        protein_FAO_perkg*w_FAO)),
   kcal_FAO_age=if_else(pregnant==1,multiplier*(kc+kc1*w_FAO+kc2*(w_FAO^2)+E_disp)+285,
                           if_else(lactating==1,multiplier*(kc+kc1*w_FAO+kc2*(w_FAO^2)+E_disp)+485,
                           multiplier*(kc+kc1*w_FAO+kc2*(w_FAO^2)+E_disp))),
    kcal_FAO_grp=if_else(pregnant==1,multiplier*(kc+kc1*w_FAO_grp+kc2*(w_FAO_grp^2)+E_disp)+285,
                           if_else(lactating==1,multiplier*(kc+kc1*w_FAO_grp+kc2*(w_FAO_grp^2)+E_disp)+485,
                           multiplier*(kc+kc1*w_FAO_grp+kc2*(w_FAO_grp^2)+E_disp))))%>%
  dplyr::rename(weight_FAO_age=w_FAO,height_FAO_age=h_FAO,weight_FAO_grp=w_FAO_grp,height_FAO_grp=h_FAO_grp,BMI_FAO_age=b_FAO)
    
    

base_FAO=FAO_energy%>%
  filter(age==18,sex==1,activity=="moderate")

base_kcal_FAO=base_FAO$kcal_FAO_age


#join FAO standards with roster
#calculate energy and protein requirements using reference and individual weights, activity adjustments for everyone
w.I.roster.2015=w.I.roster.2015%>%
 mutate(sex=as.numeric(sex))%>%
  left_join(FAO_energy,by=c("sex","age","activity","pregnant","lactating"))%>%
mutate(kcal_FAO_I=if_else(pregnant==1,multiplier*(kc+kc1*weight+kc2*(weight^2)+E_disp)+285,
                           if_else(lactating==1,multiplier*(kc+kc1*weight+kc2*(weight^2)+E_disp)+485,
                           multiplier*(kc+kc1*weight+kc2*(weight^2)+E_disp))),
       AE_FAO_I=kcal_FAO_I/base_kcal_FAO,AE_FAO_age=kcal_FAO_age/base_kcal_FAO,AE_FAO_grp=kcal_FAO_grp/base_kcal_FAO,
       BMI_FAO_age=if_else(age>18,21.5,BMI_FAO_age))%>%
  dplyr::select(-(kc:multiplier))
  

rm(list=ls(pattern="FAO"))



```


I.3 Import IOM height weight and Nutrient Requirements
```{r IOM}



library(plyr)

#DRI standards
#energy requirements
IOM_energy <- read_excel("./Data/Clean Data/nutrient standards/IOM_requirements.xlsx",sheet="Energy_IOM",range = "A1:R97",col_names = TRUE)%>% 
  mutate(sex=if_else(sex=="Male",1,2),activity=revalue(PA_level,c("sedentary"="light","low active"="light","active"="moderate","very active"="heavy")),pregnant=if_else(lifestage=="Pregnancy",1,0),lactating=if_else(lifestage=="Lactation",1,0))%>%
dplyr::select(-1,-2,-PA_level,-age_refmean,-EER_eq)%>%
dplyr::rename(agemin=age_lower_yrs,agemax=age_upper_yrs,kcal_IOM_grp=EER_IOM_ref,height_IOM_grp=refht_IOM,weight_IOM_grp=refwt_IOM)%>%
  group_by(sex,agemin,agemax,activity,pregnant,lactating)%>%
  dplyr::summarise_all(mean)%>%
  ungroup()%>%
  mutate(agemax=as.numeric(agemax))%>%
  mutate(agemax=if_else(is.na(agemax),150,agemax))

#nutrient requirements
IOM_nutrients <- read_excel("./Data/Clean Data/nutrient standards/IOM_requirements.xlsx",sheet="Nutrients",range = "A1:T23",col_names = TRUE)%>% 
#dplyr::select(-9,-11)%>% 
  mutate(sex=if_else(sex=="Male",1,2),pregnant=if_else(lifestage=="Pregnancy",1,0),lactating=if_else(lifestage=="Lactation",1,0))%>%
  dplyr::rename(agemin=age_lower_yrs,agemax=age_upper_yrs,calcium_rda_IOM=calcium_rda,calcium_ear_IOM=calcium_ear,
                iron_rda_IOM=iron_rda,iron_ear_IOM=iron_ear,
                carb_IOM_ear=carb_ear,carb_IOM_rda=carb_rda,carb_IOM_lower=carbohydrate_lower,carb_IOM_upper=carbohydrate_upper,
                protein_IOM_lower=protein_lower,protein_IOM_upper=protein_upper,protein_rda_IOM=protein_rda,
                fat_IOM_lower=lipids_lower,fat_IOM_upper=lipids_upper)%>%
  dplyr::select(-lifestage,-refht_IOM,-refwt_IOM)


base_IOM=IOM_energy%>%
  filter(agemin==19,sex==1,activity=="moderate")

base_kcal_IOM=base_IOM$kcal_IOM_grp


#join DRI energy standards with roster (calculate individual and reference requirements, everyone has activity adjustments)
w.I.roster.2015=w.I.roster.2015%>%
 fuzzy_left_join(IOM_energy,by=c("sex","age"="agemin", "age"="agemax","activity","pregnant","lactating"),match_fun=list(`==`,`>=`, `<=`,`==`,`==`,`==`))%>%
dplyr::rename(sex=sex.x,activity=activity.x,pregnant=pregnant.x,lactating=lactating.x)%>%
mutate(age_grp_IOM=if_else(!is.na(agemin),paste(as.character(agemin),as.character(agemax),sep="-"),as.character(NA)))%>%
  mutate(kcal_IOM_I=eer1-(eer2*age)+refPA*((eer3*weight)+(eer4*height/100))+eer5+eer6)%>%
  mutate(AE_IOM_grp=kcal_IOM_grp/base_kcal_IOM,AE_IOM_I=kcal_IOM_I/base_kcal_IOM)%>%
  dplyr::select(-contains(".y"),-agemin,-agemax,-refPA,-contains("eer"))
  


#generate individual and reference nutrient standards for IOM
w.I.roster.2015=w.I.roster.2015%>%
   fuzzy_left_join(IOM_nutrients,by=c("sex","age"="agemin","age"="agemax","pregnant","lactating"), match_fun=list(`==`,`>=`, `<=`,`==`,`==`))%>%
  dplyr::rename(sex=sex.x,pregnant=pregnant.x,lactating=lactating.x)%>%
    mutate(protein_ear_IOM_grp=protein_ear_perkg*weight_IOM_grp,protein_ear_IOM_I=protein_ear_perkg*weight)%>%
    dplyr::select(-contains(".y"),-protein_ear_perkg,-agemin,-agemax)

xlist=c("protein","carb")
ylist=c("lower","upper")
#zlist=c("grp","I")

for (x in xlist){
  for (y in ylist){
   # for (z in zlist){
 w.I.roster.2015[[paste(x,y,"IOM_grp",sep="_")]]<-  (w.I.roster.2015[[paste(x,"IOM",y,sep="_")]]/100)*w.I.roster.2015[[paste("kcal_IOM_grp",sep="_")]]/4

#}
}
}

xlist=c("fat")
ylist=c("lower","upper")
#zlist=c("grp","I")

for (x in xlist){
  for (y in ylist){
   # for (z in zlist){
 w.I.roster.2015[[paste(x,y,"IOM_grp",sep="_")]]<-  (w.I.roster.2015[[paste(x,"IOM",y,sep="_")]]/100)*w.I.roster.2015[[paste("kcal_IOM_grp",sep="_")]]/9

#}
}
}



w.I.roster.2015=w.I.roster.2015%>%
  dplyr::select(-contains("IOM_upper"),-contains("IOM_lower"))

rm(list=ls(pattern="IOM"),x,y,z,xlist,ylist,zlist)


```


I.4 Reference weights and Heights and add back HH variables
```{r refwtht}

#reference weights and heights
ref_wtht = w.I.roster.2015%>%
  dplyr::select(hhid,mid,sex,sampletype,age,contains("age_grp"),pregnant,lactating,contains("weight"),contains("height"),contains("code"),contains("R2"))

#add back HH-level variables and generate hh level variables
hh=w.I.roster.2015%>%
  dplyr::select(hhid,contains("AE"),-aeu)%>%
  group_by(hhid)%>%
  dplyr::summarise_all(sum,na.rm=TRUE)%>%
  dplyr::rename_at(.vars=vars(2:7),.funs=funs(sub("AE_","hhsize_",.)))
w.hh.roster.2015=left_join(w.hh.roster.2015,hh,by="hhid")

h=w.hh.roster.2015%>%
  dplyr::select(hhid,contains("hhsize_"),contains("hh_"),AE_OECD,hhds,nofood,hungryday,hungrynight)%>%
  dplyr::rename(hhsize_OECD=AE_OECD)
#task: w.I.roster.2015 does not have column named "hhsize_IOM_grp"
w.I.roster.2015=left_join(w.I.roster.2015,h,by="hhid")%>%
  mutate(share_India_grp=AE_India_grp/hhsize_India_grp,share_FAO_grp=AE_FAO_grp/hhsize_FAO_grp,share_IOM_grp=AE_IOM_grp/hhsize_IOM_grp,share_FAO_I=AE_FAO_I/hhsize_FAO_I,share_IOM_I=AE_IOM_I/hhsize_IOM_I,share_FAO_age=AE_FAO_age/hhsize_FAO_age,
         age_range=if_else(age>=2&age<4,"Toddler (2-3)", 
                           if_else(age>=4&age<8,"Young Child (4-7)",
                             if_else(age>=8&age<11,"Older Child (8-10)",
                              if_else(age>=11&age<14,"Young Adolescent (11-13)",
                              if_else(age>=14&age<18,"Older Adolescent (14-17)",
                                if_else(age>=18&age<30,"Young Adult (18-29)",
                                if_else(age>=30&age<=60,"Adult (30-59)",
                                if_else(age>60,"Older Adult (60+)",as.character(NA))))))))))


rm(h,hh,i)

```


Save household and individual rosters for analysis
```{r save, echo=FALSE}



write.csv(w.I.roster.2015,"./Programs/R/rosters/w.I.roster_2015.csv",row.names=FALSE)

write.csv(w.hh.roster.2015,"./Programs/R/rosters/w.hh.roster_2015.csv",row.names=FALSE)
```

